### 2016-03-13 paper.tex
initial commit

\documentclass[11pt]{article}

\usepackage{csquotes}
\usepackage{color}

\input{macros}

\title{Creative Destruction}
\author{Alex Ledger}
%\date{}
\pagestyle{headings}

\begin{document}
\maketitle

\section{Introduction and Old Thoughts on Creative Destruction}
Creative destruction is economic idea that refers to how new products, innovations, firms and regimes destroy old products, firms and regimes.
The idea has its roots in Marx, who questions why capitalism must destroy itself in order to exist.
Many have expanded on Marx ideas.
Most notably is Schumpeter in 1942 with his book \textit{Capitalism, Socialism and Democracy}.

Briefly, Schumpeter believes that a capitalistic economic system cannot be stationary; rather, it must be continuously in flux. 
The fundamental driver of the continuous change is new consumer good, new production methods, new markets, etc. 
The necessary new-ness of things creates ``the process of industrial mutation that incessantly revolutionizes the economic structure from within, incessantly destroying the old one, incessantly creating a new one'' \cite{wikipedia quote on schumpeter}.
Schumpter, like Marx, was skeptical of whether the creative destructive nature of capitalism was sustainable. 
Eventually, there could be too much destruction such that the system can no longer persist.

In our readings for philosophy of technology, Jaffe and Trachtenburg introduced us to concept of creative destruction.
Their aim is to formalize the idea of creative destruction and complete empirical investigations:
\begin{displayquote}
    Our aim in this paper is to create a framework for incorporating the microeconomics of creative destruction and knowledge spillovers into a model of growth, and to do so in such a way that we can begin to measure them and untangle the forces that determine their intensity and impact on growth (90)
\end{displayquote}

They analyze creative destruction empirically by using the U.S. patents database and data on market value of industries (91).
Their model is complicated, but I believe their process is straightforward enough: they correlation between patents issued from a particular sector and the market value of that sector \al{get page number on this}. 
\begin{displayquote}
    “That is, in an average sector at an average year a firm that does not invent sees its value relative to that of the industry erode by about 4\%.” (91)
\end{displayquote}

\newpage
\section{New Thoughts on Creative Destruction}
This section will discuss my thoughts on creative destruction.

\end{document}

### 2016-03-14 paper.tex
asdf

@@
 \section{Introduction and Old Thoughts on Creative Destruction}
-Creative destruction is economic idea that refers to how new products, innovations, firms and regimes destroy old products, firms and regimes.
+\subsection{Marx and Schumpter}
+Creative destruction is an economic idea that refers to how new products, innovations, firms and regimes destroy old products, firms and regimes.
 The idea has its roots in Marx, who questions why capitalism must destroy itself in order to exist.
@@
 
-In our readings for philosophy of technology, Jaffe and Trachtenburg introduced us to concept of creative destruction.
-Their aim is to formalize the idea of creative destruction and complete empirical investigations:
+\subsection{Caballero and Jaffe}
+In our readings for philosophy of technology, Caballero and Jaffe introduced us to concept of creative destruction.
+Their aim is to formalize the idea of creative destruction and knowledge spillovers and complete empirical investigations:
 \begin{displayquote}
@@
 
+Caballero and Jaffe view the economy in a schumpeterian way: ``Schumpeter recognized that innovation was the engine of growth, and that innovation is endogenously generated by competing profit-seeking firms'' (90).
+More formally, they say the economy consists of ``a continuum of monopolistically compeitive good indexed by their quality $q \in (-\infty, N_t]$''.
+In the economy, a firm that operates with constant marginal cost, i.e. a firm that does not innovating, will see their profits decline. 
+If new good are more substitutable for old goods, then the firm will see their profits decline more quickly.
+
+Beyond innovation, they are intersted in knowledge spillovers, believing that increases in public knowledge contribute to economy wide returns.
+They distinguish between knowledge and technological obselescence and creative destruction:
+\begin{displayquote}
+``Old knowledge eventually is made obsolete by the emergence of newer, superior knowledge.
+We call this phenomenon `knowledge' or `technological' obsolescence, and distinguish it from the obsolescence in value represented by creative destruction.
+That is, new ideas have two distinct effects on the current stock of ideas. 
+They make the products represented by those ideas less valuable (creative destruction or value obsolescence), and they make the knowledge represented by those ideas less relevant in the production of new knowledge (knowledge or technological obsolescence).
+The strength of knowledge spillovers, and hence the growth of the economy, will depend on the parameters of the processes of knowledge diffusion and knowledge obsolescence.'' (92)
+\end{displayquote}
+Creative destruction is specifically the effect of new innovation on the economic ``value'' of products.
+
+From a philosophy perspective, it seems overly limiting to only consider creative desturction as the impact that new creations have on the economic value of old technology.
+As a contrived example, consider Intel who sells CPUs. 
+If Intel creates
+
+\newpage
 They analyze creative destruction empirically by using the U.S. patents database and data on market value of industries (91).
@@
 \begin{displayquote}
-    “That is, in an average sector at an average year a firm that does not invent sees its value relative to that of the industry erode by about 4\%.” (91)
+    ``That is, in an average sector at an average year a firm that does not invent sees its value relative to that of the industry erode by about 4\%.'' (91)
 \end{displayquote}

### 2016-03-16 paper.tex
worked on intro of schumpeter and marx

@@
 \subsection{Marx and Schumpter}
-Creative destruction is an economic idea that refers to how new products, innovations, firms and regimes destroy old products, firms and regimes.
-The idea has its roots in Marx, who questions why capitalism must destroy itself in order to exist.
-Many have expanded on Marx ideas.
-Most notably is Schumpeter in 1942 with his book \textit{Capitalism, Socialism and Democracy}.
+This first section will introduce creative destruction.
+The idea has its roots in economics, and as such, this section will present creative destrucion in its economic form.
+In effect, this section lacks philophical rigor.
 
-Briefly, Schumpeter believes that a capitalistic economic system cannot be stationary; rather, it must be continuously in flux. 
-The fundamental driver of the continuous change is new consumer good, new production methods, new markets, etc. 
-The necessary new-ness of things creates ``the process of industrial mutation that incessantly revolutionizes the economic structure from within, incessantly destroying the old one, incessantly creating a new one'' \cite{wikipedia quote on schumpeter}.
-Schumpter, like Marx, was skeptical of whether the creative destructive nature of capitalism was sustainable. 
-Eventually, there could be too much destruction such that the system can no longer persist.
+Creative destruction is an economic idea that refers to how new products, firms and innovations destroy old products, firms and innovations.
+Neoclassical economic theory, the most popular economic theory, is built on top of the idea of equilibrium.
+Most simply, an economy has supply of things and demands of the same things. 
+Supply and demand interact with each other, creating tension between economic processes.
+The economy remains in flux until supply and demand reach a happy equilibrium.
+At a happy equilibrium, supply and demand remain more or less constant until something disrupts the system.
+
+The supply and demand theory has had strong explanatory power over the years, but it doesn't expalin one crucial observation: economies grow.
+In a neoclassical economic framework, an economy reaches equilibrium and stabilizes.
+Once an economy stabilizes, the only for it to grow is via exogenous inputs, for example, imperialism, increased supply of raw materials.
+
+However, we observe that economies grow faster than the net exogenous inputs.
+What could explain this?
+Better worded: what explains endogenous growth in an economy?
+After a close reading of Marx, Schumpeter came to the idea that innovation and entrepreneurship are the drivers of endogenous growth.
+Innovation and entrepreneurship introduce new value to the economy that did not previously exist, contributing to an overall increase in social wealth.
+However, Schumpeter also observed that new technologies (that is, the result of innovation)  and new firms often displace old technologies and old technologies.
+The new technologies and new firms are better - specifically they have a lower margincal cost or are more desirable widgets - and the old technologies lose economic value and the old firms lose profits.
+
+This the idea of creative destruction.
+The old displaces new; there is not room for both of them.
+Marx and Schumpeter had interesting concern: what if there is too much destruction by new technology such that society destroys itself.
+The capitalist system is a cycle of creation and destruction, and it seems possible, on a theoretical level, that the destruction may overwhelm the construction, spelling distaster for society.
+While on a social level this is hard to imagine, it is somewhat easier to fathom on technological level.
+
+This paper will explore the idea of creative destruction and its philosopical implications on technology. 
+To whet the appetite, a few questions that will be addressed are:
+\begin{itemize}
+    \item New technology technically does not ``destroy'' old technology; rather, it makes the old technology lose economic value.
+But, what effect does new technology have on old technology?
+Does it make it obsolete?
+Does the ``idea'' of the old technology change?
+Does the ``meaning'' of technology, which is contextual and socially constructed, changed due to a change in society or due to a change in technology?
+That question implies that technosphere, as one might call it, is distinct from society, which social constructs persuasively argue is not necessarily the case.
+    \item asdf
+\end{itemize}
 

### 2016-03-17 paper.tex
adsf
worked on section 2

@@
 \usepackage{color}
+\usepackage{amsfonts}
 
@@
 
-\section{Introduction and Old Thoughts on Creative Destruction}
+\section{Old Thoughts on Creative Destruction}
 \subsection{Marx and Schumpter}
-This first section will introduce creative destruction.
-The idea has its roots in economics, and as such, this section will present creative destrucion in its economic form.
-In effect, this section lacks philophical rigor.
+This section introduces creative destruction.
+Creative Destruction has its roots in economics, and as such, this section will present creative destruction in its economic form.
+In effect, this section lacks philosophical rigor.
 
@@
 Marx and Schumpeter had interesting concern: what if there is too much destruction by new technology such that society destroys itself.
-The capitalist system is a cycle of creation and destruction, and it seems possible, on a theoretical level, that the destruction may overwhelm the construction, spelling distaster for society.
+The capitalist system is a cycle of creation and destruction, and it seems possible, on a theoretical level, that the destruction may overwhelm the construction, spelling disaster for society.
 While on a social level this is hard to imagine, it is somewhat easier to fathom on technological level.
 
-This paper will explore the idea of creative destruction and its philosopical implications on technology. 
+This paper will explore the idea of creative destruction and its philosophical implications on technology. 
 To whet the appetite, a few questions that will be addressed are:
@@
     \item New technology technically does not ``destroy'' old technology; rather, it makes the old technology lose economic value.
-But, what effect does new technology have on old technology?
+    \item But, what effect does new technology have on old technology?
 Does it make it obsolete?
@@
 That question implies that technosphere, as one might call it, is distinct from society, which social constructs persuasively argue is not necessarily the case.
-    \item asdf
+    \item Is technology still cumulative? Or in what nuanced sense is it cumulative?
+    \item How does this idea fit into evolution?
+    \item What role does this play in selection?
+    \item Any effect on combination? gut says no, but not sure
 \end{itemize}
@@
 Caballero and Jaffe view the economy in a schumpeterian way: ``Schumpeter recognized that innovation was the engine of growth, and that innovation is endogenously generated by competing profit-seeking firms'' (90).
-More formally, they say the economy consists of ``a continuum of monopolistically compeitive good indexed by their quality $q \in (-\infty, N_t]$''.
+More formally, they say the economy consists of ``a continuum of monopolistically competitive good indexed by their quality $q \in (-\infty, N_t]$''.
 In the economy, a firm that operates with constant marginal cost, i.e. a firm that does not innovating, will see their profits decline. 
@@
 
-Beyond innovation, they are intersted in knowledge spillovers, believing that increases in public knowledge contribute to economy wide returns.
-They distinguish between knowledge and technological obselescence and creative destruction:
+Beyond innovation, they are interested in knowledge spillovers, believing that increases in public knowledge contribute to economy wide returns.
+They distinguish between knowledge and technological obsolescence and creative destruction:
 \begin{displayquote}
@@
 
-From a philosophy perspective, it seems overly limiting to only consider creative desturction as the impact that new creations have on the economic value of old technology.
+From a philosophy perspective, it seems overly limiting to only consider creative destruction as the impact that new creations have on the economic value of old technology.
 As a contrived example, consider Intel who sells CPUs. 
@@
 
-\newpage
-They analyze creative destruction empirically by using the U.S. patents database and data on market value of industries (91).
-Their model is complicated, but I believe their process is straightforward enough: they correlation between patents issued from a particular sector and the market value of that sector \al{get page number on this}.
-\begin{displayquote}
-    ``That is, in an average sector at an average year a firm that does not invent sees its value relative to that of the industry erode by about 4\%.'' (91)
-\end{displayquote}
+\section{Creative Destruction in the Theory of Technological Evolution}
+The aim of this section to situate creative destruction in the theory of technological evolution.
+Many authors have different ideas of technological evolution; however, the important components for this discussion is that there is some selection process. 
+The theory of technological evolution imagines that many technologies exist, or potential exist inside of an inventor's head, and that some social force selects which technologies are useful to humans and which aren't.
+This section will treat the aim of selection as ``use to humans'', meaning that if a technology is selected, then we say that technology was considered ``useful to humans'' in that particular social context.
+Brian Arthur was the most recent author we read to hold this view of selection.
 
-\newpage
-\section{New Thoughts on Creative Destruction}
-This section will discuss my thoughts on creative destruction.
+Creative Destruction, as described by Jaffe, is the idea that sometimes when a new technology comes into existence, the new technology decreases the economic value of an old technology. 
+\al{motivate usage of use-value over economic value}
+
+Let us take a step back for a second.
+Imagine that at some point in time, there exists technologies in the world - call this set of existing technologies $\T$. 
+Each $t \in \T$ has an use-value at this point in time. 
+Then a new technology $s$ is created.
+Upon the creation of $u$, the use-value of each technology $t$ in $\T$ is subject to change.
+The use-value of $t$ may increase, indicating that $u$ complements $t$: $u$ and $t$ function well together and make each other more valuable.
+The use-value of $t$ may stay the same, indicating the $u$ and $t$ are not related.
+Or the use-value of $t$ may decrease, indicating that $u$ substitutes $t$: $u$ may perform that same job as $t$, and hence decrease the use-value of $t$, or something along these lines ($u$ may be complementary to a replacement of $t$ - the causal relationship can be complicated).
+
+Creative destruction is concerned with the third case: where a new technology $u$ reduces the use-value of an old technology $t$.
+
+%\begin{definition}
+%Let $\T$ be the set of all existing technologies. 
+%Let $V: \T \to \RR_{\geq 0}$ be the value mapping, where $V(t)$ is the economic value of a technology.
+%Let $t$ be a new technology.
+%Then upon the existence of $t$, there exists a new value mapping $V'$, mapping technologies $\T \cup \{t\}$ to their new economic value.
+%The addition of $t$ to $\T$ affects the economic value of all technologies in $\T$.
+%\end{definition}
+
+\subsection{What is Creative Destruction and how does it fit the theory?}
+\subsection{Implications on the Theory of Technology}
+\section{Philosophical Consdiderations of Creative Destruction}
 

### 2016-03-17 paper.tex
asdf

@@
 The aim of this section to situate creative destruction in the theory of technological evolution.
-Many authors have different ideas of technological evolution; however, the important components for this discussion is that there is some selection process. 
-The theory of technological evolution imagines that many technologies exist, or potential exist inside of an inventor's head, and that some social force selects which technologies are useful to humans and which aren't.
-This section will treat the aim of selection as ``use to humans'', meaning that if a technology is selected, then we say that technology was considered ``useful to humans'' in that particular social context.
-Brian Arthur was the most recent author we read to hold this view of selection.
+Many authors have different ideas of technological evolution; however, the important component for this discussion is that there is some selection process by which fit technologies remain relevant to society.
+The aim of the selection process is an open question.
+Economists like Jaffe believe that technologies are selected because of their potential usage for economic profits \cite{jaffe}.
+Social constructivists believe that technologies are selected because of a complex causal web involving society, social conventions, economics, history, psychology and so on \cite{scot}.
+For our treatment of technological evolution, we do not believe it be too important how selection, but rather, it is important that selection occurs. 
+With this in mind, we use Brian Arthur's simple explanation of selection: a technology is useful to humans \cite{arthur}.
+We say that a particular technology has a use-value corresponding to how useful the technology is to society, humans, or the economy.
 
-Creative Destruction, as described by Jaffe, is the idea that sometimes when a new technology comes into existence, the new technology decreases the economic value of an old technology. 
-\al{motivate usage of use-value over economic value}
-
-Let us take a step back for a second.
-Imagine that at some point in time, there exists technologies in the world - call this set of existing technologies $\T$. 
-Each $t \in \T$ has an use-value at this point in time. 
-Then a new technology $s$ is created.
+We now give a formal description of the selection process using the idea of use-value. 
+At a point in time, there exist a set of technologies in society - call this set of existing technologies $\T$. 
+Each technology $t \in \T$ has an use-value at this point in time. 
+Suppose that a new technology $u$ is created.
 Upon the creation of $u$, the use-value of each technology $t$ in $\T$ is subject to change.
@@
 The use-value of $t$ may stay the same, indicating the $u$ and $t$ are not related.
-Or the use-value of $t$ may decrease, indicating that $u$ substitutes $t$: $u$ may perform that same job as $t$, and hence decrease the use-value of $t$, or something along these lines ($u$ may be complementary to a replacement of $t$ - the causal relationship can be complicated).
+Or the use-value of $t$ may decrease, indicating that $u$ substitutes $t$: $u$ may perform that same job as $t$, and hence decrease the use-value of $t$, or something along these lines ($u$ may be complementary to a replacement of $t$ - the causal relationship can be complicated)
+\footnote{We assume that use-value is 1-dimensional value: a use-value can go up or down, but not left and right. 
+This simplification appears to be fine, but in the future, it may be useful to think of useful as a vector in vector space, allowing for more abstraction relationships and changes.}.
 
 Creative destruction is concerned with the third case: where a new technology $u$ reduces the use-value of an old technology $t$. 
+Biologists identify a similar process to creative destruction occurring in the selection of species. 
+The phenomenon is called \textit{competitive exclusion}. 
+Competitive exclusion is the idea that if two species are competing for the same resource, then one of the species will overcome the other, forcing the other species to adapt or die \cite{wiki-competitive-exclusion}.
+In recent years, observational, experimental and simulation-based evidence has surfaced to cause Biologists to question the simplicity of competitive exclusion.
+We did not examine the new evidence close enough to explain here.
+
+There is a strong a parallel between creative destruction and competitive exclusion.
+To use the terms of Biology, two technologies cannot coexist and rely on the same resources for their use-value, so one must either die or adapt. 
+Technologies do not die or adapt per se, rather they either become irrelevant.
+And it is still an unanswered question whether a technology adapts. 
+To Biologists, the subject which is adapting is the species, and there is no straightforward analog of a species in technology. 
+We ignore the issue and say there is no concept of a species in technology); rather, when a technology adapts in response to competition, the technology is really giving birth a new technology, and that new technology is more fit than its parent.
+
+The story of competitive exclusion applies well to the story of creative destruction.
+Does the opposite hold true?
+A technologist (us)
 

### 2016-03-17 paper.tex
asdf

@@
 Does the opposite hold true?
-A technologist (us)
+A technologist (us) would say that upon the creation of a new species (or upon the creation of a new adaptation of a species) the use-value of all other species are affected, and species whose use-values decline are in some sense destroyed.
+The use-value in this context is fitness - reproductive success.
+The species whose fitness declines sufficiently may become extinct; otherwise, the species adapt, changing their fitness. 
+The story seems of creative destruction also seems to apply well to competitive exclusion.
 
-%\begin{definition}
-%Let $\T$ be the set of all existing technologies. 
-%Let $V: \T \to \RR_{\geq 0}$ be the value mapping, where $V(t)$ is the economic value of a technology.
-%Let $t$ be a new technology.
-%Then upon the existence of $t$, there exists a new value mapping $V'$, mapping technologies $\T \cup \{t\}$ to their new economic value.
-%The addition of $t$ to $\T$ affects the economic value of all technologies in $\T$.
-%\end{definition}
+The one caveat in both stories is the usage of use-value and fitness. 
+The definition of use-value given at the beginning of this section focused on how useful a certain technology was to society. 
+This idea has no direct relation to the reproductive power of a given technology. 
+A technology that is more likely to reproduce is likely correlated to its use-value (although that would need to be tested empirically), but there exist technologies whose use-value remains high but they do not reproduce.
+The best example of this is the MRI.
+The MRI was invented in the 1970s, and since then it has been used widely (i.e. high/constant use-value), but few people have innovated on top of it (i.e. low reproductive success). 
+It is quite possible that the MRI is an anomaly, and that in general, reproductive success is strongly correlated to use-value. 
+We believe this to be true.
+Use-value is highly correlated to reproductive success, and use-value is a sufficient metric of fitness.
 
-\subsection{What is Creative Destruction and how does it fit the theory?}
+If use-value and reproductive success are not highly correlated, then there are a number of steps one could take.
+First, one could use reproductive success instead of use-value when describing selection and creative destruction. 
+The theory would likely hold, but there many be detailed differences. 
+Second, one could use this as support than technological evolution is not darwinian: the important factor in technological evolution is not reproduction but rather the use-value of a technology
+\footnote{This is an interesting idea. Reproductive power may not be a central component of evolutionary systems.}.
+
 \subsection{Implications on the Theory of Technology}
-\section{Philosophical Consdiderations of Creative Destruction}
+\section{Philosophical Considerations of Creative Destruction}
 

### 2016-03-18 paper.tex
added sources
asdf

@@
 The aim of the selection process is an open question.
-Economists like Jaffe believe that technologies are selected because of their potential usage for economic profits \cite{jaffe}.
+Economists like Jaffe believe that technologies are selected because of their potential for economic profits \cite{jaffe}.
 Social constructivists believe that technologies are selected because of a complex causal web involving society, social conventions, economics, history, psychology and so on \cite{scot}.
@@
 The phenomenon is called \textit{competitive exclusion}. 
-Competitive exclusion is the idea that if two species are competing for the same resource, then one of the species will overcome the other, forcing the other species to adapt or die \cite{wiki-competitive-exclusion}.
+Competitive exclusion is the idea that if two species are competing for the same resource, then one of the species will overcome the other, forcing the other species to adapt or die \cite{wiki}. 
 In recent years, observational, experimental and simulation-based evidence has surfaced to cause Biologists to question the simplicity of competitive exclusion.
@@
 The theory would likely hold, but there many be detailed differences. 
-Second, one could use this as support than technological evolution is not darwinian: the important factor in technological evolution is not reproduction but rather the use-value of a technology
+Second, one could use this as support that technological evolution is not darwinian: the important factor in technological evolution is not reproduction but rather the use-value of a technology
 \footnote{This is an interesting idea. Reproductive power may not be a central component of evolutionary systems.}.
@@
 \subsection{Implications on the Theory of Technology}
+This section discusses the implications of creative destruction on the theory of technology.
+
+The first implication of creative destruction is that faster invention creation results in faster destruction.
+The idea is that as society innovates more, creates new inventions, then there is simultaneously a destruction of old technology. 
+And since society is innovating more, presubly there is more destruction.
+There may be a net-effect of more innovation, but it is important that destruction may increase in periods of rapid innovation.
+This suggests that technology is subject a phenomenon like Newton's third law: the more technology there is, the greater the push-back on old technology.
+
+The second implication of creative destruction is that there could be a net-decrease in technology. 
+The idea of creative destruction leaves open the possibility that more technologies are destroyed than are created.
+That being said, as far as we are aware, a net-decrease in technology has not been observed.
+Yet this is an idea that worred Marx and Schumpeter, albeit their concern was with capitalism not technology.
+Marx and Schumpeter worried that capitalism would destroy itself; there would be so much sudden growth destroying the old system, and the system would collapse.
+
+We find it imaginable that a new series of technology destroy old technology too quickly, rendering the new and old technology useless.
+Consider many sudden innovations to the internet.
+The internet is a highly complex, abstract, layered, decentralized web of interactions on which much technology relies.
+One could imagine that we, society, decide to improve the internet, but improve it such that the old infrastructure is destroyed and the new infrastructure insufficient or incomplete.
+We, society, have buried ourselves into a hole.
+We, society, don't have reliable technology to use. 
+We can't simply reimplement the old internet because it is too intertwined, too complicated.
+And we can't use the new internet for whatever reason.
+In the end, more was destroyed than created.
+
 \section{Philosophical Considerations of Creative Destruction}
+This section discusses philosophical considerations of creative destruction.
+We outline three philosphical implications.
+
+First, creative destruction makes technology more unpredictable.
+The reason for this hearkens back to Brian Arthur's idea of primitives. 
+Arthur reasons that new technology is the product of a new combination of primitives. 
+Creative destruction
+
+\bibliographystyle{apalike}
+\bibliography{paper}
 

### 2016-03-18 paper.tex
asdf

@@
 
-The supply and demand theory has had strong explanatory power over the years, but it doesn't expalin one crucial observation: economies grow.
+The supply and demand theory doesn't explain one crucial observation: economies grow.
 In a neoclassical economic framework, an economy reaches equilibrium and stabilizes.
@@
 This the idea of creative destruction.
-The old displaces new; there is not room for both of them.
-Marx and Schumpeter had interesting concern: what if there is too much destruction by new technology such that society destroys itself.
+The old displaces new; the better, more efficient verison makes the old, costly version unviable.
+For example, the smartphone, sophisticated little computer with the power the text and call, destroyed the economic viability of the dumb-phone.
+Marx and Schumpeter were concerned about the possible effects of creative destruction: what if there is too much destruction?
 The capitalist system is a cycle of creation and destruction, and it seems possible, on a theoretical level, that the destruction may overwhelm the construction, spelling disaster for society.
-While on a social level this is hard to imagine, it is somewhat easier to fathom on technological level.
-
-This paper will explore the idea of creative destruction and its philosophical implications on technology. 
-To whet the appetite, a few questions that will be addressed are:
-\begin{itemize}
-    \item New technology technically does not ``destroy'' old technology; rather, it makes the old technology lose economic value.
-    \item But, what effect does new technology have on old technology?
-Does it make it obsolete?
-Does the ``idea'' of the old technology change?
-Does the ``meaning'' of technology, which is contextual and socially constructed, changed due to a change in society or due to a change in technology?
-That question implies that technosphere, as one might call it, is distinct from society, which social constructs persuasively argue is not necessarily the case.
-    \item Is technology still cumulative? Or in what nuanced sense is it cumulative?
-    \item How does this idea fit into evolution?
-    \item What role does this play in selection?
-    \item Any effect on combination? gut says no, but not sure
-\end{itemize}
 
@@
 Creative destruction is specifically the effect of new innovation on the economic ``value'' of products.
+Caballero and Jaffe measures the effect on innovation on industries by using market value and patent data on 567 large U.S. firms.
+They found that:
+\begin{displayquote}
+    ``In an average sector at an average year a firm that does not invent sees it relative value to that of the industry erode by about 4\%.''
+\end{displayquote}
+That is, there is approximately 4\% destruction of pre-existing technology on average per year. 
+Different industries observed varying levels of destruction.
+On the high end, the pharmaceutical industry observed 25\% destruction per year, yet multiple sectors observed 0\% destruction.
 
-From a philosophy perspective, it seems overly limiting to only consider creative destruction as the impact that new creations have on the economic value of old technology.
-As a contrived example, consider Intel who sells CPUs. 
-If Intel creates
+We find Caballero and Jaffe's method to be interesting and the results to be useful, but the story is not yet complete.
+The model that Caballero and Jaffe use to compute creative destruction\footnote{The model is not communicated in this paper} is complicated and computed over a short number of years.
+However, the findings are consistent with intuition.
+4\% destruction on average per year is a reasonable number, and it is to be expected that pharmaceuticals see a high level destruction relative to other industries. 
+Further research could be done on the economic side of creative destruction.
+First, Jaffe and Caballero could further investigate the nature of the technologies that are being destroyed, charactering the nature of the destruction (e.g.
+is it intra-firm created, extra-firm created, expected destruction, unexpected destruction, and so on.).
+Second, it would be interesting to measure creative destruction using other methods, for example using research and development expenditures.
+Third, it would be interesting to see how the industries are effected by the varying degrees of creative destruction, and the way that the firms innovate.
+
+We greatly appreciate Caballero and Jaffe's results, and use them to motivate our research and argue about the effects of creative destruction.
 
@@
 The reason for this hearkens back to Brian Arthur's idea of primitives. 
-Arthur reasons that new technology is the product of a new combination of primitives. 
-Creative destruction
+Arthur reasons that new technology is the product of a new combination of tecnological primitives. 
+At a given time, there exists a set of primitives. 
+A new technology is created out of recombining the existing primitives, that the new technology is added to set of the primitives.
+Creative destruction suggests that when a new technology is created and added to the set of primitives, pre-existing technologies may be removed from the set of primitives.
+The primitives interact with each other - some in a complementary way and some in a supplementary way (like creative destruction). 
+When one is trying to predict the future path of technology, the primitives available in the future may be missing primitves that are present now, making the task substantially more complex.
+
+Second, creative destruction does introduce a feeling that technology is dangerous.
+Mark and Schumpeter worried that society would create so much that it would consume and destroy itself, and this is a possibility with technology.
+In section 2, we outlined an example of how the internet may be destroyed if there is too much innovation too fast.
+New technology, introduced and implmented in the wrong way, could undermine the technological infrastructure that has been built up. 
+With the technological infrastructure gone, it's not difficult to imagine the negative social reprecussions.
+
+Third, we have the perhaps unfortunate situation where there is constantly new technology.
+New iphones, new computers, new drugs.
+With the creation of each new invention, creative destruction theory says that old technology may be destroyed.
+The old technology, which was likely less expensive (for various reason), is now inaccessible: all that exists is the new, expensive technology.
+The implication is that the poor, who cannot afford the new technology, are left with nothing. 
+In cases, the poor can't afford the new technology, and the old technology, which they may or may not be able to afford, no longer exists.
+
+The most pressing area where we see this problem is the pharmaceutical industry.
+There are two phases for a drug on the market. 
+The first phase is where the drug is patented, the firm has a monopoloy on it and prices are high.
+The second phase is after the patent expires, and the drug enters the public domain. 
+Unfortunatley, some drugs don't benefit from the second phase. 
+\footnote{I did not look up examples and examine this in detail.}
+There are cases where people don't benefit from drugs being the second phase.
+It is not economically viable for firms to mass produce the drug, so poorer people can't access it.
+
+\section{Conclusion}
+Creative Destruction, the idea that new technologies make existing technologies less relevant, fits in nicely with the technological theory of evolution.
+In particular, creative destruction explains a portion of the selection process, and how new technologies affect the fitness landscape of existing technologies.
+Moreover, creative destruction has a strong analog in biological evolution, competitive exclusion.
+Creative destruction and competitive exclusion share many commonalities and few differences, but the similarities suggest that at least some part of technological selection is quite similar to biological selection.
+
+Creative destruction also brings three philosophical considerations to the table: (1) technology is complex and unpredictable, (2) technology is potential dangerous to itself and (3) the nature of technology is classist, harming the poor in some instances.
+We consider the third point to be most important and most easily observed.
+Technology has the power to do great good and great harm. 
+The good and harm can stem from individual technologies themselves, like a technology that cures cancer is great, but drones that kill humans are arguably bad. 
+Zooming out, the nature of technology and how it evolves has a devestating effect on the poor.
+The poor cannot afford the new technologies, and the new technologies often cause firms to not produce old technologies because they are not economically viable, leaving the poor without anything. 
+Here, it is the process by which technology is created and evolves which harms the poor, not the technology itself.
 

### 2016-03-20 paper.tex
cat edits/revisions

@@
 %\date{}
-\pagestyle{headings}
+\pagestyle{myheadings}
 
@@
 Creative Destruction has its roots in economics, and as such, this section will present creative destruction in its economic form.
-In effect, this section lacks philosophical rigor.
 
-Creative destruction is an economic idea that refers to how new products, firms and innovations destroy old products, firms and innovations.
 Neoclassical economic theory, the most popular economic theory, is built on top of the idea of equilibrium.
@@
 In a neoclassical economic framework, an economy reaches equilibrium and stabilizes.
-Once an economy stabilizes, the only for it to grow is via exogenous inputs, for example, imperialism, increased supply of raw materials.
+Once an economy stabilizes, the only way for it to grow is via exogenous inputs, for example, increased supply of raw materials.
 
@@
 Innovation and entrepreneurship introduce new value to the economy that did not previously exist, contributing to an overall increase in social wealth.
-However, Schumpeter also observed that new technologies (that is, the result of innovation)  and new firms often displace old technologies and old technologies.
+However, Schumpeter also observed that new technologies (that is, the result of innovation)  and new firms often displace old technologies and old firms.
 The new technologies and new firms are better - specifically they have a lower margincal cost or are more desirable widgets - and the old technologies lose economic value and the old firms lose profits.
@@
 This the idea of creative destruction.
-The old displaces new; the better, more efficient verison makes the old, costly version unviable.
-For example, the smartphone, sophisticated little computer with the power the text and call, destroyed the economic viability of the dumb-phone.
+The old displaces new; the better, more efficient verison makes the old, costly version economically unviable.
+For example, the smartphone, a sophisticated little computer with the power to text and call, destroyed the economic viability of the dumb-phone.
+
 Marx and Schumpeter were concerned about the possible effects of creative destruction: what if there is too much destruction?
@@
 \begin{displayquote}
-    Our aim in this paper is to create a framework for incorporating the microeconomics of creative destruction and knowledge spillovers into a model of growth, and to do so in such a way that we can begin to measure them and untangle the forces that determine their intensity and impact on growth (90)
+    ``Our aim in this paper is to create a framework for incorporating the microeconomics of creative destruction and knowledge spillovers into a model of growth, and to do so in such a way that we can begin to measure them and untangle the forces that determine their intensity and impact on growth'' \cite{jaffe} (90)
 \end{displayquote}
 
-Caballero and Jaffe view the economy in a schumpeterian way: ``Schumpeter recognized that innovation was the engine of growth, and that innovation is endogenously generated by competing profit-seeking firms'' (90).
-More formally, they say the economy consists of ``a continuum of monopolistically competitive good indexed by their quality $q \in (-\infty, N_t]$''.
-In the economy, a firm that operates with constant marginal cost, i.e. a firm that does not innovating, will see their profits decline. 
-If new good are more substitutable for old goods, then the firm will see their profits decline more quickly.
+Caballero and Jaffe view the economy in a Schumpeterian way: ``Schumpeter recognized that innovation was the engine of growth, and that innovation is endogenously generated by competing profit-seeking firms'' (90).
+More formally, they say the economy consists of ``a continuum of monopolistically competitive goods indexed by their quality $q \in (-\infty, N_t]$''.
+In the economy, a firm that operates with constant marginal cost, i.e. a firm that does not innovate, will see their profits decline. 
+If new goods are more substitutable for old goods, then the firm will see their profits decline more quickly.
 
-Beyond innovation, they are interested in knowledge spillovers, believing that increases in public knowledge contribute to economy wide returns.
-They distinguish between knowledge and technological obsolescence and creative destruction:
-\begin{displayquote}
-``Old knowledge eventually is made obsolete by the emergence of newer, superior knowledge.
-We call this phenomenon `knowledge' or `technological' obsolescence, and distinguish it from the obsolescence in value represented by creative destruction.
-That is, new ideas have two distinct effects on the current stock of ideas. 
-They make the products represented by those ideas less valuable (creative destruction or value obsolescence), and they make the knowledge represented by those ideas less relevant in the production of new knowledge (knowledge or technological obsolescence).
-The strength of knowledge spillovers, and hence the growth of the economy, will depend on the parameters of the processes of knowledge diffusion and knowledge obsolescence.'' (92)
-\end{displayquote}
-Creative destruction is specifically the effect of new innovation on the economic ``value'' of products.
-Caballero and Jaffe measures the effect on innovation on industries by using market value and patent data on 567 large U.S. firms.
+To Caballero and Jaffe, creative destruction is specifically the effect of new innovation on the economic ``value'' of existing products.
+They measure the effect of innovation on industries by using market value data and patent data on 567 large U.S. firms.
 They found that:
 \begin{displayquote}
-    ``In an average sector at an average year a firm that does not invent sees it relative value to that of the industry erode by about 4\%.''
+    ``In an average sector at an average year a firm that does not invent sees it relative value to that of the industry erode by about 4\%.'' \cite{jaffe}
 \end{displayquote}
@@
 4\% destruction on average per year is a reasonable number, and it is to be expected that pharmaceuticals see a high level destruction relative to other industries. 
+The source of profits for pharmaceutical, drugs, require a large amount of capital investment, and failure to continue to research results in other firms pulling ahead: an example of the red queen game.
+\footnote{A reference to \textit{Alice in Wonderland}, and a game-theory-economic idea for firms needing to continuously invest in order to not fall behind.}
+
 Further research could be done on the economic side of creative destruction.
-First, Jaffe and Caballero could further investigate the nature of the technologies that are being destroyed, charactering the nature of the destruction (e.g.
+First, Jaffe and Caballero could further investigate the nature of the technologies that are being destroyed, characterizing the nature of the destruction (e.g.
 is it intra-firm created, extra-firm created, expected destruction, unexpected destruction, and so on.).
 Second, it would be interesting to measure creative destruction using other methods, for example using research and development expenditures.
-Third, it would be interesting to see how the industries are effected by the varying degrees of creative destruction, and the way that the firms innovate.
+Third, it would be interesting to see how the industries are affected by the varying degrees of creative destruction, and the way that the firms innovate.
 
@@
 
-\section{Creative Destruction in the Theory of Technological Evolution}
+\section{Creative Destruction in the Theory of Technology}
+\subsection{Situating Creative Destruction in Theory of Technological Evolution}
 The aim of this section to situate creative destruction in the theory of technological evolution.
@@
 Social constructivists believe that technologies are selected because of a complex causal web involving society, social conventions, economics, history, psychology and so on \cite{scot}.
-For our treatment of technological evolution, we do not believe it be too important how selection, but rather, it is important that selection occurs. 
-With this in mind, we use Brian Arthur's simple explanation of selection: a technology is useful to humans \cite{arthur}.
-We say that a particular technology has a use-value corresponding to how useful the technology is to society, humans, or the economy.
+For our treatment of technological evolution, we do not believe it to be too important \textit{how} selection occurs, but rather, it is important \textit{that} selection occurs. 
+With this in mind, we use Brian Arthur's simple explanation of selection: technologies that are useful to humans are selected \cite{arthur}.
+We say that a particular technology has use-value corresponding to how useful the technology is to society, humans, or the economy.
 
@@
 At a point in time, there exist a set of technologies in society - call this set of existing technologies $\T$. 
-Each technology $t \in \T$ has an use-value at this point in time. 
+Each technology $t \in \T$ has use-value at this point in time. 
 Suppose that a new technology $u$ is created.
@@
 \footnote{We assume that use-value is 1-dimensional value: a use-value can go up or down, but not left and right. 
-This simplification appears to be fine, but in the future, it may be useful to think of useful as a vector in vector space, allowing for more abstraction relationships and changes.}.
+This simplification appears to be fine, but in the future, it may be useful to think of use-value as a vector in vector space, allowing for more abstract relationships.}.
+Creative destruction is concerned with the third case: where a new technology $u$ reduces the use-value of an old technology $t$.
 
-Creative destruction is concerned with the third case: where a new technology $u$ reduces the use-value of an old technology $t$. 
-Biologists identify a similar process to creative destruction occurring in the selection of species. 
+In order to further understand creative destruction, we compare the negative selection process in technological evolution to the negative selection process in biological evolution.
+Interestingly, biologists identify a similar process to creative destruction occurring in the selection of species.
 The phenomenon is called \textit{competitive exclusion}. 
 Competitive exclusion is the idea that if two species are competing for the same resource, then one of the species will overcome the other, forcing the other species to adapt or die \cite{wiki}. 
-In recent years, observational, experimental and simulation-based evidence has surfaced to cause Biologists to question the simplicity of competitive exclusion.
-We did not examine the new evidence close enough to explain here.
+In recent years, observational, experimental and simulation-based evidence has surfaced to cause biologists to question the simplicity of competitive exclusion.
+We did not examine the new evidence close enough to explain here, but it seems that the general idea of competitive exclusion remains true.
 
 There is a strong a parallel between creative destruction and competitive exclusion.
-To use the terms of Biology, two technologies cannot coexist and rely on the same resources for their use-value, so one must either die or adapt. 
-Technologies do not die or adapt per se, rather they either become irrelevant.
-And it is still an unanswered question whether a technology adapts. 
-To Biologists, the subject which is adapting is the species, and there is no straightforward analog of a species in technology. 
-We ignore the issue and say there is no concept of a species in technology); rather, when a technology adapts in response to competition, the technology is really giving birth a new technology, and that new technology is more fit than its parent.
+To use the terms of biology, two technologies cannot coexist and rely on the same resources for their use-value, so one must either die or adapt. 
+To biologists, the subject which is adapting is the species, and there is no straightforward analog of a species in technology. 
+Technologies, in contrast, do not die or adapt per se, rather they become irrelevant.
+When a technology responds to competition, the technology is births a new technology, and that new technology is more fit than its parent.
 
@@
 The species whose fitness declines sufficiently may become extinct; otherwise, the species adapt, changing their fitness. 
-The story seems of creative destruction also seems to apply well to competitive exclusion.
+The story of creative destruction also seems to apply well to competitive exclusion.
 
@@
 The definition of use-value given at the beginning of this section focused on how useful a certain technology was to society. 
-This idea has no direct relation to the reproductive power of a given technology. 
-A technology that is more likely to reproduce is likely correlated to its use-value (although that would need to be tested empirically), but there exist technologies whose use-value remains high but they do not reproduce.
+This idea has no clear causal relation to the reproductive power of a given technology. 
+A technology's use-value is likely correlated to its reproductive power (although that would need to be tested empirically)
+That being said,there are examples of technologies whose use-value remains high but do not reproduce. 
 The best example of this is the MRI.
-The MRI was invented in the 1970s, and since then it has been used widely (i.e. high/constant use-value), but few people have innovated on top of it (i.e. low reproductive success). 
+The MRI was invented in the 1970s, and since then it has been used widely (i.e. high/constant use-value).
+However, there are few innovations on top of the MRI (i.e. low reproductive success). 
 It is quite possible that the MRI is an anomaly, and that in general, reproductive success is strongly correlated to use-value. 
 We believe this to be true.
-Use-value is highly correlated to reproductive success, and use-value is a sufficient metric of fitness.
-
-If use-value and reproductive success are not highly correlated, then there are a number of steps one could take.
-First, one could use reproductive success instead of use-value when describing selection and creative destruction. 
-The theory would likely hold, but there many be detailed differences. 
-Second, one could use this as support that technological evolution is not darwinian: the important factor in technological evolution is not reproduction but rather the use-value of a technology
-\footnote{This is an interesting idea. Reproductive power may not be a central component of evolutionary systems.}.
+Thus we assume use-value is highly correlated to reproductive success, and as such, use-value is a sufficient metric of fitness.
 
@@
 The first implication of creative destruction is that faster invention creation results in faster destruction.
-The idea is that as society innovates more, creates new inventions, then there is simultaneously a destruction of old technology. 
-And since society is innovating more, presubly there is more destruction.
-There may be a net-effect of more innovation, but it is important that destruction may increase in periods of rapid innovation.
-This suggests that technology is subject a phenomenon like Newton's third law: the more technology there is, the greater the push-back on old technology.
+The reason for this hearkens back to Brian Arthur's idea of primitives. 
+Arthur reasons that new technology is the product of a new combination of tecnological primitives. 
+At a given time, there exists a set of primitives. 
+A new technology is created out of recombining the existing primitives, then the new technology is added to set of the primitives.
+Creative destruction suggests that when a new technology is created and added to the set of primitives, the new primitives may be complemented or subistuted (i.e. their use-value goes up or down).
+If a primitives use-value goes sufficiently down, then the primitive may become irrelevant to society and cease to be a primitive.
+
+Now consider that more and more primitives are being created. 
+Then more existing primitives are liable to lose their use-value and be destroyed.
+Technology is subject a phenomenon like Newton's third law: the more technology there is, the greater the push-back on old technology.
 
 The second implication of creative destruction is that there could be a net-decrease in technology. 
-The idea of creative destruction leaves open the possibility that more technologies are destroyed than are created.
+Consider the range of possibible technologies that given set of primitives allows or leads to.
+Since primitives are being destroyed and as new primitives are created, it is possible that the range of primitives decreases - there's no clear justification for believing the range of possibilities monotonically increases.
+
 That being said, as far as we are aware, a net-decrease in technology has not been observed.
@@
 
-We find it imaginable that a new series of technology destroy old technology too quickly, rendering the new and old technology useless.
-Consider many sudden innovations to the internet.
+As an example, imagine if there were many sudden innovations to the internet.
 The internet is a highly complex, abstract, layered, decentralized web of interactions on which much technology relies.
@@
 We can't simply reimplement the old internet because it is too intertwined, too complicated.
-And we can't use the new internet for whatever reason.
+And we can't use the new internet because the new technology turned out to be too complicated or insufficient.
 In the end, more was destroyed than created.
@@
 First, creative destruction makes technology more unpredictable.
-The reason for this hearkens back to Brian Arthur's idea of primitives. 
-Arthur reasons that new technology is the product of a new combination of tecnological primitives. 
-At a given time, there exists a set of primitives. 
-A new technology is created out of recombining the existing primitives, that the new technology is added to set of the primitives.
 Creative destruction suggests that when a new technology is created and added to the set of primitives, pre-existing technologies may be removed from the set of primitives.
-The primitives interact with each other - some in a complementary way and some in a supplementary way (like creative destruction). 
 When one is trying to predict the future path of technology, the primitives available in the future may be missing primitves that are present now, making the task substantially more complex.
 
-Second, creative destruction does introduce a feeling that technology is dangerous.
-Mark and Schumpeter worried that society would create so much that it would consume and destroy itself, and this is a possibility with technology.
+Second, creative destruction introduces a feeling that technology is dangerous.
+Marx and Schumpeter worried that society would create so much that it would consume and destroy itself, and this is a possibility with technology.
 In section 2, we outlined an example of how the internet may be destroyed if there is too much innovation too fast.
-New technology, introduced and implmented in the wrong way, could undermine the technological infrastructure that has been built up. 
+New technology, introduced and implemented in the wrong way, could undermine the technological infrastructure that has been built up. 
 With the technological infrastructure gone, it's not difficult to imagine the negative social reprecussions.
@@
 With the creation of each new invention, creative destruction theory says that old technology may be destroyed.
-The old technology, which was likely less expensive (for various reason), is now inaccessible: all that exists is the new, expensive technology.
+The old technology, which is likely less expensive now, is now inaccessible: all that exists is the new, expensive technology.
 The implication is that the poor, who cannot afford the new technology, are left with nothing. 
-In cases, the poor can't afford the new technology, and the old technology, which they may or may not be able to afford, no longer exists.
+In some cases, the poor can't afford the new technology, and the old technology, which they may be able to afford, no longer exists.
 
@@
 The second phase is after the patent expires, and the drug enters the public domain. 
-Unfortunatley, some drugs don't benefit from the second phase. 
-\footnote{I did not look up examples and examine this in detail.}
-There are cases where people don't benefit from drugs being the second phase.
-It is not economically viable for firms to mass produce the drug, so poorer people can't access it.
+Unfortunatley, poor people don't benefit from drugs being in the second phase, because the existence of the new technology disincentivizes firms from selling post-patent drugs \footnote{There are many post-patent drugs that are sold on the market, but remarkably fewer than the number of useful, invented drugs.}.
 
@@
 Moreover, creative destruction has a strong analog in biological evolution, competitive exclusion.
-Creative destruction and competitive exclusion share many commonalities and few differences, but the similarities suggest that at least some part of technological selection is quite similar to biological selection.
+Creative destruction and competitive exclusion share many commonalities and few differences, suggesting that at least some part of technological selection is quite similar to biological selection.
 
@@
 Technology has the power to do great good and great harm. 
-The good and harm can stem from individual technologies themselves, like a technology that cures cancer is great, but drones that kill humans are arguably bad. 
+The good and harm can stem from individual technologies themselves, in the way that technology that cures cancer is great, but drones that kill humans are arguably bad. 
 Zooming out, the nature of technology and how it evolves has a devestating effect on the poor.

### 2016-03-20 paper.tex
nearly final version

@@
 \section{Old Thoughts on Creative Destruction}
-\subsection{Marx and Schumpter}
+\subsection{Marx and Schumpeter}
 This section introduces creative destruction.
@@
 Neoclassical economic theory, the most popular economic theory, is built on top of the idea of equilibrium.
-Most simply, an economy has supply of things and demands of the same things. 
+Most simply, an economy has supply of things and demands of things. 
 Supply and demand interact with each other, creating tension between economic processes.
@@
 Better worded: what explains endogenous growth in an economy?
-After a close reading of Marx, Schumpeter came to the idea that innovation and entrepreneurship are the drivers of endogenous growth.
-Innovation and entrepreneurship introduce new value to the economy that did not previously exist, contributing to an overall increase in social wealth.
-However, Schumpeter also observed that new technologies (that is, the result of innovation)  and new firms often displace old technologies and old firms.
-The new technologies and new firms are better - specifically they have a lower margincal cost or are more desirable widgets - and the old technologies lose economic value and the old firms lose profits.
+After a close reading of Marx, Schumpeter came to the idea that innovation and entrepreneurship are the drivers of endogenous growth \cite{jaffe}.
+Innovation and entrepreneurship introduce new value into the economy that did not previously exist, contributing to an overall increase in social wealth.
+Schumpeter also observed that new technologies (that is, the results of innovation)  and new firms often displace old technologies and old firms.
+The new technologies and new firms are economically better - specifically they have a lower marginal cost or are more desirable widgets - and the old technologies lose economic value and the old firms lose profits.
+If the old technology and old firms lose sufficient value or profits respectively, then they cease to remain part of the economic system.
 
 This the idea of creative destruction.
-The old displaces new; the better, more efficient verison makes the old, costly version economically unviable.
+The old displaces new; the better, more efficient version makes the old, costly version economically unviable.
 For example, the smartphone, a sophisticated little computer with the power to text and call, destroyed the economic viability of the dumb-phone.
-
-Marx and Schumpeter were concerned about the possible effects of creative destruction: what if there is too much destruction?
-The capitalist system is a cycle of creation and destruction, and it seems possible, on a theoretical level, that the destruction may overwhelm the construction, spelling disaster for society.
 
@@
 Caballero and Jaffe view the economy in a Schumpeterian way: ``Schumpeter recognized that innovation was the engine of growth, and that innovation is endogenously generated by competing profit-seeking firms'' (90).
-More formally, they say the economy consists of ``a continuum of monopolistically competitive goods indexed by their quality $q \in (-\infty, N_t]$''.
 In the economy, a firm that operates with constant marginal cost, i.e. a firm that does not innovate, will see their profits decline. 
-If new goods are more substitutable for old goods, then the firm will see their profits decline more quickly.
+If a firm's goods are more substitutable for new goods, then the firm will see their profits decline more quickly.
 
@@
 However, the findings are consistent with intuition.
-4\% destruction on average per year is a reasonable number, and it is to be expected that pharmaceuticals see a high level destruction relative to other industries. 
-The source of profits for pharmaceutical, drugs, require a large amount of capital investment, and failure to continue to research results in other firms pulling ahead: an example of the red queen game.
-\footnote{A reference to \textit{Alice in Wonderland}, and a game-theory-economic idea for firms needing to continuously invest in order to not fall behind.}
+4\% destruction on average per year is a reasonable number, and it is to be expected that pharmaceuticals see a high level of destruction relative to other industries. 
+The source of profits of pharmaceutical firms, drugs, requires a large amount of capital investment, and a firm's failure to continue to research results in other firms pulling ahead.
 
 Further research could be done on the economic side of creative destruction.
-First, Jaffe and Caballero could further investigate the nature of the technologies that are being destroyed, characterizing the nature of the destruction (e.g.
+First, one could further investigate the nature of the technologies that are being destroyed, characterizing the nature of the destruction (e.g.
 is it intra-firm created, extra-firm created, expected destruction, unexpected destruction, and so on.).
@@
 With this in mind, we use Brian Arthur's simple explanation of selection: technologies that are useful to humans are selected \cite{arthur}.
-We say that a particular technology has use-value corresponding to how useful the technology is to society, humans, or the economy.
+We say that a particular technology has use-value corresponding to how useful the technology is to society, humans or the economy.
 
 We now give a formal description of the selection process using the idea of use-value. 
-At a point in time, there exist a set of technologies in society - call this set of existing technologies $\T$. 
+At a point in time, there exists a set of technologies in society - call this set of existing technologies $\T$. 
 Each technology $t \in \T$ has use-value at this point in time. 
@@
 The use-value of $t$ may stay the same, indicating the $u$ and $t$ are not related.
-Or the use-value of $t$ may decrease, indicating that $u$ substitutes $t$: $u$ may perform that same job as $t$, and hence decrease the use-value of $t$, or something along these lines ($u$ may be complementary to a replacement of $t$ - the causal relationship can be complicated)
+Or the use-value of $t$ may decrease, indicating that $u$ substitutes $t$: $u$ may perform the same job as $t$, and hence decrease the use-value of $t$, or something along these lines (the causal relationship can be complicated - e.g.
+$u$ may be complementary to a replacement of $t$)
 \footnote{We assume that use-value is 1-dimensional value: a use-value can go up or down, but not left and right. 
@@
 In order to further understand creative destruction, we compare the negative selection process in technological evolution to the negative selection process in biological evolution.
-Interestingly, biologists identify a similar process to creative destruction occurring in the selection of species.
+Interestingly, biologists identify a similar process to creative destruction in the selection of species.
 The phenomenon is called \textit{competitive exclusion}. 
@@
 Technologies, in contrast, do not die or adapt per se, rather they become irrelevant.
-When a technology responds to competition, the technology is births a new technology, and that new technology is more fit than its parent.
+When a technology responds to competition, the technology births new technology, and that new technology is more fit than its parent.
 
@@
 The one caveat in both stories is the usage of use-value and fitness. 
-The definition of use-value given at the beginning of this section focused on how useful a certain technology was to society. 
-This idea has no clear causal relation to the reproductive power of a given technology. 
-A technology's use-value is likely correlated to its reproductive power (although that would need to be tested empirically)
-That being said,there are examples of technologies whose use-value remains high but do not reproduce. 
+The definition of use-value given at the beginning of this section focuses on how useful a certain technology is to society. 
+Use-value has no clear causal relation to the reproductive power of a given technology. 
+A technology's use-value is likely correlated to its reproductive power (although that would need to be tested empirically).
+That being said, there are examples of technologies whose use-value remains high but do not reproduce. 
 The best example of this is the MRI.
@@
 The reason for this hearkens back to Brian Arthur's idea of primitives. 
-Arthur reasons that new technology is the product of a new combination of tecnological primitives. 
+Arthur reasons that new technology is the product of a new combination of technological primitives. 
 At a given time, there exists a set of primitives. 
 A new technology is created out of recombining the existing primitives, then the new technology is added to set of the primitives.
-Creative destruction suggests that when a new technology is created and added to the set of primitives, the new primitives may be complemented or subistuted (i.e. their use-value goes up or down).
-If a primitives use-value goes sufficiently down, then the primitive may become irrelevant to society and cease to be a primitive.
+Creative destruction suggests that when a new technology is created and added to the set of primitives, the new primitives may be complemented or substituted (i.e. their use-value goes up or down).
+If a primitive's use-value sufficiently decreases, then the primitive may become irrelevant to society and cease to be a primitive.
 
@@
 The second implication of creative destruction is that there could be a net-decrease in technology. 
-Consider the range of possibible technologies that given set of primitives allows or leads to.
-Since primitives are being destroyed and as new primitives are created, it is possible that the range of primitives decreases - there's no clear justification for believing the range of possibilities monotonically increases.
+Consider the range of possible technologies that given set of primitives allows or leads to.
+Since primitives are destroyed as new primitives are created, it is possible that the range of primitives decreases - there's no clear justification for believing the range of possibilities monotonically increases.
 
 That being said, as far as we are aware, a net-decrease in technology has not been observed.
-Yet this is an idea that worred Marx and Schumpeter, albeit their concern was with capitalism not technology.
-Marx and Schumpeter worried that capitalism would destroy itself; there would be so much sudden growth destroying the old system, and the system would collapse.
+Yet this is an idea that worried Marx and Schumpeter, albeit their concern was with capitalism not technology.
+Marx and Schumpeter worried that capitalism would destroy itself; large amounts of creation would lead to overwhelming amounts of destruction, and consequently, the system would collapse on itself.
 
@@
 One could imagine that we, society, decide to improve the internet, but improve it such that the old infrastructure is destroyed and the new infrastructure insufficient or incomplete.
-We, society, have buried ourselves into a hole.
-We, society, don't have reliable technology to use. 
+We have buried ourselves into a hole.
+We don't have reliable technology to use. 
 We can't simply reimplement the old internet because it is too intertwined, too complicated.
-And we can't use the new internet because the new technology turned out to be too complicated or insufficient.
+And we can't use the new internet because the new technology turned out to be too complicated or be insufficient.
 In the end, more was destroyed than created.
@@
 This section discusses philosophical considerations of creative destruction.
-We outline three philosphical implications.
+We outline three philosophical implications.
 
@@
 Creative destruction suggests that when a new technology is created and added to the set of primitives, pre-existing technologies may be removed from the set of primitives.
-When one is trying to predict the future path of technology, the primitives available in the future may be missing primitves that are present now, making the task substantially more complex.
+When one is trying to predict the future path of technology, the primitives available in the future may be missing primitives that are present now, making the task substantially more complex.
 
@@
 New technology, introduced and implemented in the wrong way, could undermine the technological infrastructure that has been built up. 
-With the technological infrastructure gone, it's not difficult to imagine the negative social reprecussions.
+With the technological infrastructure gone, it's not difficult to imagine the negative social repercussions.
 
 Third, we have the perhaps unfortunate situation where there is constantly new technology.
-New iphones, new computers, new drugs.
+New iPhones, new computers, new drugs.
 With the creation of each new invention, creative destruction theory says that old technology may be destroyed.
 The old technology, which is likely less expensive now, is now inaccessible: all that exists is the new, expensive technology.
-The implication is that the poor, who cannot afford the new technology, are left with nothing. 
-In some cases, the poor can't afford the new technology, and the old technology, which they may be able to afford, no longer exists.
+The implication is that the poor are left with nothing. 
+The poor cannot afford the new technology, and the old technology, which they may be able to afford, no longer exists.
 
@@
 There are two phases for a drug on the market. 
-The first phase is where the drug is patented, the firm has a monopoloy on it and prices are high.
+The first phase is where the drug is patented, the firm has a monopoly on it and prices are high.
 The second phase is after the patent expires, and the drug enters the public domain. 
-Unfortunatley, poor people don't benefit from drugs being in the second phase, because the existence of the new technology disincentivizes firms from selling post-patent drugs \footnote{There are many post-patent drugs that are sold on the market, but remarkably fewer than the number of useful, invented drugs.}.
+Unfortunately, poor people don't benefit from drugs being in the second phase, because the existence of the new technology disincentivizes firms from selling post-patent drugs \footnote{There are many post-patent drugs that are sold on the market, but remarkably fewer than the number of useful, invented drugs.}.
 
@@
 The good and harm can stem from individual technologies themselves, in the way that technology that cures cancer is great, but drones that kill humans are arguably bad. 
-Zooming out, the nature of technology and how it evolves has a devestating effect on the poor.
+Zooming out, the nature of technology and how it evolves has a devastating effect on the poor.
 The poor cannot afford the new technologies, and the new technologies often cause firms to not produce old technologies because they are not economically viable, leaving the poor without anything. 

### 2016-05-05 encryption/paper.tex
adding begginings of Enc paper

\documentclass[11pt]{article}

\usepackage{csquotes}
\usepackage{color}
\usepackage{amsfonts}

\input{macros}

\title{Creative Destruction in the Philosophy of Technology}
\author{Alex Ledger}
\date{}
\pagestyle{myheadings}

\begin{document}
\maketitle

\section{Introduction}
Over the last few years, namely since the Snowden revelations in 2013, issues concerning privacy, anonymity and surveillence on the internet have come to the forefront of our cultural discussions.
Snowden surprised many people when he said provided evidence that the NSA has access to our internet activity, and moreover, the NSA may read our email, a mode of communication that we commonly considered to be private.
Due to this new information, many persons seeking privacy from the government resorted to using \textit{encrytion} to protect their privacy.
Encryption is means of obfuscating a message - if two people use encryption, they can talk to each other without an eavesdropper reading their message, or with extra pre-cautions, from learning their identities.

With the advent of the Snowden revelations came the slogan, ``you have nothing worry about if you have nothing to hide,'' in effect painting encryption as unpatriotic act of rebellion.

Another debate has emerged over how encryption may undermine the efforts of the law-enforcement community: encryption allows criminals to communicate, allowing them to elude law-enforcement and hence presenting a security risk to the citizenry.
Law-enforcement argues in favor of restricting the power of encryption, and in particular, requiring that all encryption used within the United States have some kind of master-key.
The master-key, which the company providing the encrpytion would hold (e.g., Apple or Google), would allow the law-enforcement agency to unlock encrypted messages.

The goal of this paper is to take a step back from the politicized arguments surrounding encryption and anonymity and ask a basic question: do we have a right to encryption?
Is ethically permissible to restrict public access to encryption, or is it unethical to give criminals easy-access to encryption?
\al{Talk about structure of paper}

\section{Background}
In order to discuss encryption from an ethical perspective, I first give background information on encryption.
Encryption has been around for centuries; we have evidence from centuries ago that various armies use some form of encryption, and more recently and famously, Hitler used the engima machine in World War II to obfuscate messages between his troops.
It is only recently that encryption has been described as an act of rebellion, and something that should potentially be restricted; my suspicion is that the main reason for this that we all know have access to encryption, as opposed to states, and so it needs to be restricted, perhaps to support a state that uses surveillence.

It is interesting, to me as a cryptographer, that we believe we can \textit{restrict} encryption.
Encryption is at its core a mathematical fact.
If I want to talk to you, we can both do some math and communicate secretly, as simple as that: math enables use to communicate privately.
To restrict encryption really means to restrict the type of encryption schemes that governments who offer encryption in their products use.
For example, Apple, who encrypts users' messages sent over iMessage, could be restricted to using an encryption that uses a master-key.
If Apple does not use an encryption scheme with a master-key, a regulatory body could fine Apple for not abiding by the encryption regulations.
To me, it seems like a clear overreach for the government to prevent me from doing encryption on my own: writing an encryption scheme is Python, and communicating with a friend using my own program.
The difference here is that I am not selling my encryption; I am simply using math.
I would imagine that this would be allowed by freedom of speech - the freedom to write a program - but I have been surprised by laws and court decisions before.

The final fact to be aware of is that by requiring encryption schemes that use a master-key, the governemnt would greatly weaken the cyber-security infrastructure.
As we have seen, it is not too difficult for hackers, either private or state-sponsored, to break into databases, and in theory, steal the master-key, giving them access to all \textit{private} messages encrypted using that master-key.

%\bibliographystyle{apalike}
%\bibliography{paper}

\end{document}

### 2016-05-05 encryption/paper.tex
asdf

@@
 \usepackage{amsfonts}
+\usepackage{setspace}
 
@@
 \begin{document}
+\doublespacing
+
 \maketitle
@@
 
+\section{Parallel Situations}
+To think about whether encryption is a fundamental right, it helps to think about parallel situations to communicated via encryption.
+Encryption, as I will be thinking about it, is a method that allows two or more parties to send messages over the internet without an eavesdropper from reading, or learning any information about, the contents of the messages.
+Encryption is also used to obfuscate data on a laptop or iPhone, such as in the recent case between the FBI and Apple, but I believe that it will simplify our reasoning if we leave that situation to another day.
+
+One way to think about encryption is verbally talking to another party in a private room, in which case we ask the question: if we are alone in a private room with another party, do we have the right to communicate privately - that is, do we have a right to \textit{not} be eavesdropped on?
+The legal answer to this question turns out, somewhat unsuprisingly, to be complex and situatational.
+The law varies based on the state, but if you are talking in a business setting and the organization hosting the conversation makes a reasonable effort to inform the parties that they are being audio-visually recorded, then it is legal.
+% https://www.quora.com/Is-it-legal-to-bug-a-workplace-conference-room-in-the-US
+Let us ignore the case of a business, and consider a private residence: it is my lay understanding that homes can only be audio-visually surveilled if the law-enforcement body acquires a warrant, and it is illegal for a private-party to audio-visually surveil a private residence.
+
 %\bibliographystyle{apalike}

### 2016-05-08 encryption/paper.tex
8 pages

--- 2016-05-05 encryption/paper.tex
@@
 If I want to talk to you, we can both do some math and communicate secretly, as simple as that: math enables use to communicate privately.
-To restrict encryption really means to restrict the type of encryption schemes that governments who offer encryption in their products use.
-For example, Apple, who encrypts users' messages sent over iMessage, could be restricted to using an encryption that uses a master-key.
+To restrict encryption really means to restrict the type of encryption schemes that firms who offer encryption in their products use.
+For example, Apple, who encrypts users' messages sent over iMessage, could be restricted to using an encryption scheme that uses a master-key.
 If Apple does not use an encryption scheme with a master-key, a regulatory body could fine Apple for not abiding by the encryption regulations.
-To me, it seems like a clear overreach for the government to prevent me from doing encryption on my own: writing an encryption scheme is Python, and communicating with a friend using my own program.
-The difference here is that I am not selling my encryption; I am simply using math.
-I would imagine that this would be allowed by freedom of speech - the freedom to write a program - but I have been surprised by laws and court decisions before.
+
+In contrast, the government could prevent any person from using encryption schemes with certain properties, like me using an encryption scheme that I implement myself in Python and use to communicate with my friend.
+The difference between this situation and Apple in the previous paragraph is that I am not selling encrpytion; rather, I am simply doing math.
+I believe that regulating encryption on the indvidiaul level is clearly a governmental overreach.
+I would imagine that such regulations would be illegal by freedom of speech - the freedom to write a program - but I have been surprised by laws and court decisions before.
 
@@
 As we have seen, it is not too difficult for hackers, either private or state-sponsored, to break into databases, and in theory, steal the master-key, giving them access to all \textit{private} messages encrypted using that master-key.
+
+\section{Parallel Situations}
+In this section we present a variety of situations that are similar and disimilar to encryption to help us think about whether we have a fundamental right to encrytion.
+
+First a few definitions.
+Encryption, as I will be thinking about it, is a method that allows two or more parties to send messages over the internet without an eavesdropper from reading, or learning any information about, the contents of the messages.
+Encryption is also used to obfuscate data on a laptop or iPhone, such as in the recent case between the FBI and Apple, but I believe that it will simplify our reasoning if we leave that situation to another day.
+
+\al{other definitions if needed}
+
+\subsubsection{Private Room, Private Converstation}
+One way to think about encryption is verbally talking to another party in a private room, in which case we ask the question: if we are alone in a private room with another party, do we have the right to communicate privately - that is, do we have a right to \textit{not} be eavesdropped on?
+To avoid annoying criticisms, let us further assume that we are in a private residence, talking in a soundproof room, and we, the conversors, have received no indication that someone might be listening to our conversation.
+In this case, it seems reasonable for us to expect a private conversation - if you take issue with this, then you may ignore the following analysis.
+
+\subsubsection{Private Room, Crowded Conversation}
+
+We now expand the hypothetical situation to be more similar to encryption.
+Instead suppose that we are in a private residence in a crowded room. 
+I am standing on one side of the room, and the person to whom I am speaking is standing on the other side.
+We wish to communicate without others in the room from listening. 
+We can achieve this using public-key encryption: we can each do some math, shout at each other, let everyone listen to our shouts, and in the end communicate some message that everyone else is oblivious to.
+
+The question now is, do we have a right to have a private conversation in this room despite the fact that there are others in the room listening?
+The answer to this question is less clear to me than the private-room-private-conversation question.
+For instance, it seems weird that we expect to have a private conversation in such a situation: why would we not move to a different room to talk privately?
+On the other hand, if we assume that room is public and  we don't have access to a private room, then if we want to have a private conversation, we are required to use public-key encryption.
+This situation is much more similar to using encryption over the internet: the internet is accessible to the public, so in order to converse privately over the internet, we are required to use public-key encryption.
+
+\subsubsection{Mail}
+
+The internet can be thought of as a means to communicate over a large distance in a short amount of time, like an optimized form of mail.
+I write an email, send it to you via the internet, and you receive the message and open.
+Since the internet runs on a public system - packets get passed around from server to server - anyone who comes across my email in the process of it getting to you could read its contents.
+Therefore, the only way to communicate privately with you is to use some form of encryption.
+
+The matter is complicated by the fact that we don't \textit{own} the internet; the internet is run by private firms and the government, and they let us use it (for a price, or taxes). 
+This makes communicating over the internet similar to communicating via the United States Post Service USPS.
+I give my letter to the USPS and a desired destination, the USPS does internal work to get the letter to the destination, and you eventually receive the letter.
+In this framing, it feels like the USPS is doing me a favor; they are doing the hard word and heavy lifting, and I am using their convenient service.
+
+We naturally ask the question, do we have a right to privacy when we send a letter using the postal service?
+Does the postal service have the right to open up my letter and read it?
+I believe - but may be wrong - that most people feel that the USPS should not be able to open my letter and read it. 
+My letter is private, and I am paying them for their communication services, so they should communicate my letter without meddling.
+
+If the USPS does have the right to read letters, do I have a right to encrypt the contents my letter?
+Probably, but if the justification for reading letters appeals to national security, then I may not have the same right to encryption.
+National security effort need to be able to read my letter if it's bad, so I don't have a right to encrypt it.
+This line of reasoning returns to the slogan, ``you have nothing to worry about if you have nothing to hide.''
+
+Another way to think about the USPS reading letters is to think about the question using business ethics.
+First, I formalize the proble.
+Suppose the USPS were a private company that performs a service $S$.
+Service $S$ takes as input $x$, outputs $S(x)$.
+In the process of performing $S$, the USPS does not need to know anything about $x$.
+In fact, I put $x$ into an envelope or letter, call this $l(x)$.
+I actually give the USPS $l(x)$ and they return $S(l(x))$.
+The question then is if the USPS does not need to open $l(x)$ (i.e., reveal $x$) in order to perform $S$, then do they have any right to do so?
+
+In a general business setting, I expect that a business will perform what I ask of them with minimal intrusion into inputs.
+I am paying them to perform the service, and not to investigate me.
+Perhaps it is reasonable to say that the business can learn some information about $x$ during processing the service, but the amount of that they learn about $x$ should be upper bounded by some value.
+That is, they can learn some things, because it's unreasonable to hold them an absurdly high standard of respecting my privacy, but they shouldn't go out of their way to learn about my input.
+
+That being said, the case of the USPS and the internet is different because it's the government that is performing the service.
+The aim of the government is to aid the people, and this specific case, their foremost goal is deliver my letter or internet request.
+In this light, it seems unreasonable for the USPS or internet provider to open my envelope to read its contents, unless there is some other priority such as national security, which becomes a messier issue.
+
+\subsubsection{National Security}
+Many arguments for regulating encryption focus on the fact that weaker encryption would aid national security efforts.
+This argument is difficult to address for various reasons.
+However, I recall hearing that Snowden revealed that little to none of the NSA's privacy-invading efforts had contributed to national security.
+And that many of the privacy breaches were justified under the guise of national security, but in fact had other uses and purposes.
+To me, this debate in part boils down the efficacy.
+There is some sweet spot where privacy and national security are optimized, but the public does not have adequate information to truly assess this problem, as we do not details about national security efforts or privacy invasion.
 

### 2016-05-09 encryption/paper.tex
asdf

@@
 \subsubsection{National Security}
-Many arguments for regulating encryption focus on the fact that weaker encryption would aid national security efforts.
+Many arguments for regulating encryption focus on the fact that strong encryption helps criminals undermine national security efforts.
 This argument is difficult to address for various reasons.
@@
 
+\section{Summing it up}
+The last section, instead of providing a clear answer to question of encryption, brought up some important points that need to be addressed in order to come to satisfying answer.
+The aim of this section is to highlight those points, as they should be useful to future work.
+
+The first point is that sending messages over the internet is different from talking.
+When people communicate via the internet, the messages are publicly accessible (to some extent), since they bounce from server to server on their way to their destination.
+Talking on the internet is fundamentally different from two parties talking in a private room; rather, they are talking in a crowded room.
+Then, the only possible method by which the parties can achieve privacy is by using public-key encryption, but we must first ask the question: do people have a right to a private conversation in a crowded room?
+In a real world, non-internet setting, I'm inclined to say no. 
+By trying to have a conversation in a crowded room, the parties would inconvenience others, for example by requiring that others steer clear of the section of the room in which the parties are conversing.
+But what if the parties do not inconvenience anyone when having their conversation?
+Encryption on the internet does not inconvenience those with whom the parties am not communicating.
+My conclusion is that there is no easy way to compare encryption to talking.
+At any point, there are differences such that we, as philosophers, lose the ethical importance of the matter when we try to draw parallels.
+
+The second point is really a sub-problem that needs to be addressed to resolve the encryption question.
+The sub-problem asks, ``do the institutions that run the internet have the right to read the contents of the messages they are handling?''
+In section 3.0.3 I introduced formal notation for what it means to send a message $x$ over the internet.
+When a message is sent over the internet, we put the internet into an envelope, creating $l(x)$, such that for the handlers of the internet to read the message they need to open the envelope.
+In the real world, opening the envelope could take many forms; for example, the handlers of the internet could simply save the message after they process it; such an action is above and beyond the duty of the runners of the internet - they do not need to save the message to perform their job, and it doesn't even help them perform their job better - so we should consider such an action as not required.
+This sub-problem is can likely be addressed by appealing to business ethics: to what extent can a business investigate the input to a request from a client without violating the client's privacy?
+
+The third point is that national security is an important consideration.
+Undoubtedly, the internet and encryption could be used to organize events that we have a moral responsibility to prevent, if it is within our power.
+This question ultimatley asks how do we balance the trade-off between national security and privacy.
+Many parties from many perspectives have different beliefs on this question, and I imagine that the problem will continue to be contentious for years to come.
+
+%
+%- Sending messages over the internet is different from talking.
+%    - Same room private conversation
+%    - Same public conversation
+%- Does a business or government have the right to open an envelope?
+%    - Goes back to business ethics and what is infrastructure
+%- National security
+%    - At what point do we have unequivocal right to privacy that trumps any national security argument?
+
+\section{Conclusion}
+We need to address many other problems before we can come to a good understanding and conclusion to whether we have a right to use encryption over the internet.
+The aim of this paper was to start a formal process for thinking through the question.
+Another easy step forward is see how the arguments for and against encryption fall into the tropes of new and emerging science technology (NEST) ethics.
+We refer the reader to \cite{nest}, a good overview of NEST ethics and common responses.
+
 %\bibliographystyle{apalike}

### 2016-05-09 encryption/paper.tex
adwf

@@
 Over the last few years, namely since the Snowden revelations in 2013, issues concerning privacy, anonymity and surveillence on the internet have come to the forefront of our cultural discussions.
-Snowden surprised many people when he said provided evidence that the NSA has access to our internet activity, and moreover, the NSA may read our email, a mode of communication that we commonly considered to be private.
+Snowden surprised many people when he provided evidence that the NSA has access to our internet activity and specifically that the NSA may read our email, a mode of communication that we commonly considered to be private.
 Due to this new information, many persons seeking privacy from the government resorted to using \textit{encrytion} to protect their privacy.
-Encryption is means of obfuscating a message - if two people use encryption, they can talk to each other without an eavesdropper reading their message, or with extra pre-cautions, from learning their identities.
+Encryption is means of obfuscating a message - if two people use encryption, they can talk to each other without worrying that an eavesdropper might be reading their messages.
+In response to this, the phrase ``you have nothing worry about if you have nothing to hide'' became a slogan for those in support of the NSA; in effect, the slogan and idea it represents paints encryption as unpatriotic act of rebellion.
 
-With the advent of the Snowden revelations came the slogan, ``you have nothing worry about if you have nothing to hide,'' in effect painting encryption as unpatriotic act of rebellion.
-
-Another debate has emerged over how encryption may undermine the efforts of the law-enforcement community: encryption allows criminals to communicate, allowing them to elude law-enforcement and hence presenting a security risk to the citizenry.
+Another debate has emerged over how encryption may undermine the efforts of the law-enforcement community: encryption enables criminals to communicate such that law-enforcement cannot read their messages and hence presenting a national security risk.
 Law-enforcement argues in favor of restricting the power of encryption, and in particular, requiring that all encryption used within the United States have some kind of master-key.
-The master-key, which the company providing the encrpytion would hold (e.g., Apple or Google), would allow the law-enforcement agency to unlock encrypted messages.
+The master-key, which the company providing the encrpytion would hold (e.g., Apple or Google), would allow the law-enforcement agency to decrypt encrypted messages.
 
 The goal of this paper is to take a step back from the politicized arguments surrounding encryption and anonymity and ask a basic question: do we have a right to encryption?
-Is ethically permissible to restrict public access to encryption, or is it unethical to give criminals easy-access to encryption?
-\al{Talk about structure of paper}
+This question is difficult to answer or even approach, and as such, this paper does not answer the question, but it introduces sub-problems that need to be addressed first.
+The hope was that some formalism of the encryption may come to fruition, but unfortunately, none was produced.
+However, this paper is a good starting point for thinking about encryption, and is useful for future, rigorous work.
 
@@
 Encryption has been around for centuries; we have evidence from centuries ago that various armies use some form of encryption, and more recently and famously, Hitler used the engima machine in World War II to obfuscate messages between his troops.
-It is only recently that encryption has been described as an act of rebellion, and something that should potentially be restricted; my suspicion is that the main reason for this that we all know have access to encryption, as opposed to states, and so it needs to be restricted, perhaps to support a state that uses surveillence.
+It is only recently that groups believe that encryption should be restricted; my suspicion is that the main reason for this that we all know have access to encryption, as opposed to states, and so it needs to be restricted, perhaps to support a state that uses surveillence.
 
-It is interesting, to me as a cryptographer, that we believe we can \textit{restrict} encryption.
+It is interesting to me as a cryptographer that we believe we can \textit{restrict} encryption.
 Encryption is at its core a mathematical fact.
-If I want to talk to you, we can both do some math and communicate secretly, as simple as that: math enables use to communicate privately.
+If I want to talk to you, we can both do some math and communicate secretly, as simple as that.
 To restrict encryption really means to restrict the type of encryption schemes that firms who offer encryption in their products use.
@@
 If Apple does not use an encryption scheme with a master-key, a regulatory body could fine Apple for not abiding by the encryption regulations.
+If encryption does become regulated, I predict that some interesting black-market app will appear that performs the same essential functionality as Whatsapp.
 
-In contrast, the government could prevent any person from using encryption schemes with certain properties, like me using an encryption scheme that I implement myself in Python and use to communicate with my friend.
+The government can feasibly regulate the market, but they cannot regulate individual practices.
+For example, it's hard to imagine the government could successfully prevent any person from using encryption schemes with certain properties, like me using an encryption scheme that I implement myself in Python and use to communicate with my friend.
 The difference between this situation and Apple in the previous paragraph is that I am not selling encrpytion; rather, I am simply doing math.
-I believe that regulating encryption on the indvidiaul level is clearly a governmental overreach.
-I would imagine that such regulations would be illegal by freedom of speech - the freedom to write a program - but I have been surprised by laws and court decisions before.
+I would imagine that reguations on indivudal encryption would be disallowed by freedom of speech - the freedom to write a program - but I have been surprised by laws and court decisions before.
 
@@
 \section{Parallel Situations}
-In this section we present a variety of situations that are similar and disimilar to encryption to help us think about whether we have a fundamental right to encrytion.
-
-First a few definitions.
-Encryption, as I will be thinking about it, is a method that allows two or more parties to send messages over the internet without an eavesdropper from reading, or learning any information about, the contents of the messages.
+In this section we present a variety of situations that are similar and disimilar to encryption to help us think about whether we have a right to use encrytion over the internet.
+Encryption, as I will be using it, is a method that allows two or more parties to send messages over the internet without an eavesdropper from reading, or learning any information about, the contents of the messages.
 Encryption is also used to obfuscate data on a laptop or iPhone, such as in the recent case between the FBI and Apple, but I believe that it will simplify our reasoning if we leave that situation to another day.
 
-\al{other definitions if needed}
-
 \subsubsection{Private Room, Private Converstation}
-One way to think about encryption is verbally talking to another party in a private room, in which case we ask the question: if we are alone in a private room with another party, do we have the right to communicate privately - that is, do we have a right to \textit{not} be eavesdropped on?
-To avoid annoying criticisms, let us further assume that we are in a private residence, talking in a soundproof room, and we, the conversors, have received no indication that someone might be listening to our conversation.
-In this case, it seems reasonable for us to expect a private conversation - if you take issue with this, then you may ignore the following analysis.
+If we are alone in a private room with another party, do we have the right to communicate privately - that is, do we have a right to \textit{not} be eavesdropped on?
+To avoid annoying criticisms, let us further assume that we are in a private residence, talking in a soundproof room, and the conversors have received no indication that someone might be listening to our conversation.
+In this case, it seems reasonable to expect a private conversation; I will operate under this assumption going forward.
+However, the internet is not a private room with only two parties but a crowded space.
 
@@
 Instead suppose that we are in a private residence in a crowded room. 
-I am standing on one side of the room, and the person to whom I am speaking is standing on the other side.
-We wish to communicate without others in the room from listening. 
-We can achieve this using public-key encryption: we can each do some math, shout at each other, let everyone listen to our shouts, and in the end communicate some message that everyone else is oblivious to.
+One party stands on one side of the room, and the other party stands on the other side.
+The parties wish to communicate without others in the room from listening.
+The parties can achieve this using public-key encryption: each party can do some math, shout at each other, let everyone listen to their shouts, and in the end communicate some message that everyone else is oblivious to.
 
@@
 The internet can be thought of as a means to communicate over a large distance in a short amount of time, like an optimized form of mail.
-I write an email, send it to you via the internet, and you receive the message and open.
+I write an email, send it to you via the internet, and you receive the email and read it.
 Since the internet runs on a public system - packets get passed around from server to server - anyone who comes across my email in the process of it getting to you could read its contents.
@@
 
-The matter is complicated by the fact that we don't \textit{own} the internet; the internet is run by private firms and the government, and they let us use it (for a price, or taxes). 
+The matter is complicated by the fact that we don't \textit{own} the internet; the internet is run by private firms and the government, and they let us use it (for a price or taxes). 
 This makes communicating over the internet similar to communicating via the United States Post Service USPS.

### 2016-05-10 encryption/paper.tex
asdf

@@
 Encryption is means of obfuscating a message - if two people use encryption, they can talk to each other without worrying that an eavesdropper might be reading their messages.
-In response to this, the phrase ``you have nothing worry about if you have nothing to hide'' became a slogan for those in support of the NSA; in effect, the slogan and idea it represents paints encryption as unpatriotic act of rebellion.
+In response to this, the phrase ``you have nothing worry about if you have nothing to hide'' became a slogan for those in support of the NSA; in effect, the slogan and idea it represents paint encryption as unpatriotic act of rebellion.
 
@@
 Law-enforcement argues in favor of restricting the power of encryption, and in particular, requiring that all encryption used within the United States have some kind of master-key.
-The master-key, which the company providing the encrpytion would hold (e.g., Apple or Google), would allow the law-enforcement agency to decrypt encrypted messages.
+The master-key, which the company providing the encrpytion would hold (e.g., Apple or Google), would allow law-enforcement agencies to decrypt encrypted messages.
 
@@
 This question is difficult to answer or even approach, and as such, this paper does not answer the question, but it introduces sub-problems that need to be addressed first.
-The hope was that some formalism of the encryption may come to fruition, but unfortunately, none was produced.
-However, this paper is a good starting point for thinking about encryption, and is useful for future, rigorous work.
+This paper is a good starting point for thinking about encryption, and is useful for future, rigorous work.
 
@@
 In order to discuss encryption from an ethical perspective, I first give background information on encryption.
-Encryption has been around for centuries; we have evidence from centuries ago that various armies use some form of encryption, and more recently and famously, Hitler used the engima machine in World War II to obfuscate messages between his troops.
-It is only recently that groups believe that encryption should be restricted; my suspicion is that the main reason for this that we all know have access to encryption, as opposed to states, and so it needs to be restricted, perhaps to support a state that uses surveillence.
+Encryption has been around for centuries; we have evidence from centuries ago that various armies used some form of encryption, and more recently and famously, Hitler used the engima machine in World War II to obfuscate messages between his troops.
+It is only recently that society questions unrestricted encryption; my suspicion is that the main reason for this that we all know have access to encryption, as opposed to only states having access, and so encryption needs to be restricted, perhaps to support a state that uses surveillence.
 
@@
 The government can feasibly regulate the market, but they cannot regulate individual practices.
-For example, it's hard to imagine the government could successfully prevent any person from using encryption schemes with certain properties, like me using an encryption scheme that I implement myself in Python and use to communicate with my friend.
-The difference between this situation and Apple in the previous paragraph is that I am not selling encrpytion; rather, I am simply doing math.
+For example, it is hard to imagine that the government could successfully prevent any person from using encryption schemes with certain properties, like me using an encryption scheme that I implement myself in Python and use to communicate with my friend.
+The difference between this situation and Apple in the previous paragraph is that I am not selling encrpytion.
 I would imagine that reguations on indivudal encryption would be disallowed by freedom of speech - the freedom to write a program - but I have been surprised by laws and court decisions before.
 
-The final fact to be aware of is that by requiring encryption schemes that use a master-key, the governemnt would greatly weaken the cyber-security infrastructure.
+By requiring encryption schemes that use a master-key, the governemnt would greatly weaken the cyber-security infrastructure.
 As we have seen, it is not too difficult for hackers, either private or state-sponsored, to break into databases, and in theory, steal the master-key, giving them access to all \textit{private} messages encrypted using that master-key.
@@
 \section{Parallel Situations}
-In this section we present a variety of situations that are similar and disimilar to encryption to help us think about whether we have a right to use encrytion over the internet.
+A common place to start when thinking about the ethics of encryption is to compare encryption to more common ethical situations such as talking or sending a letter.
+The aim of this section is to introduce and discuss these situations.
+We find that the hypothetical situations are useful but are not strong parallels to the actual usage of encryption, and as such they are not conclusive.
+
 Encryption, as I will be using it, is a method that allows two or more parties to send messages over the internet without an eavesdropper from reading, or learning any information about, the contents of the messages.
@@
 To avoid annoying criticisms, let us further assume that we are in a private residence, talking in a soundproof room, and the conversors have received no indication that someone might be listening to our conversation.
-In this case, it seems reasonable to expect a private conversation; I will operate under this assumption going forward.
-However, the internet is not a private room with only two parties but a crowded space.
+In this case, it seems reasonable to expect a private conversation.
+However, the internet is not a private room with only two parties; rather, it may be considered a crowded place, so this hypothetical situation lacks a strong parellel to actual usage of encryption.
 
@@
 Instead suppose that we are in a private residence in a crowded room. 
-One party stands on one side of the room, and the other party stands on the other side.
-The parties wish to communicate without others in the room from listening.
-The parties can achieve this using public-key encryption: each party can do some math, shout at each other, let everyone listen to their shouts, and in the end communicate some message that everyone else is oblivious to.
+I stand on one side of the room, and the other conversor stands on the other side.
+We wish to communicate without others in the room from listening.
 
@@
 For instance, it seems weird that we expect to have a private conversation in such a situation: why would we not move to a different room to talk privately?
-On the other hand, if we assume that room is public and  we don't have access to a private room, then if we want to have a private conversation, we are required to use public-key encryption.
-This situation is much more similar to using encryption over the internet: the internet is accessible to the public, so in order to converse privately over the internet, we are required to use public-key encryption.
+On the other hand, if we assume that room is public and we don't have access to a private room, then we need to section of a portion of the room for our private use.
+This would inconvience others in the room, only for the sake of our private conversation.
+In some situations, if our private conversation is critical for the people in the room, then it is justified for us to inconvenience the others, but in general, it does not seem justified.
+It does not seem that we necessarily have a right to a private conversation; the right to the private conversation is situational.
 
@@
 This makes communicating over the internet similar to communicating via the United States Post Service USPS.
-I give my letter to the USPS and a desired destination, the USPS does internal work to get the letter to the destination, and you eventually receive the letter.
-In this framing, it feels like the USPS is doing me a favor; they are doing the hard word and heavy lifting, and I am using their convenient service.
+I give my letter to the USPS and tell them a desired destination, the USPS does internal work to get the letter to the destination, and you eventually receive the letter.
+In this framing, the USPS is doing the hard word and heavy lifting, and I am using their convenient service.
 
@@
 If the USPS does have the right to read letters, do I have a right to encrypt the contents my letter?
-Probably, but if the justification for reading letters appeals to national security, then I may not have the same right to encryption.
-National security effort need to be able to read my letter if it's bad, so I don't have a right to encrypt it.
-This line of reasoning returns to the slogan, ``you have nothing to worry about if you have nothing to hide.''
+Probably, but if the justification for reading letters is strong (e.g., it appeals to national security), then I may not have the same right to encryption.
 
 Another way to think about the USPS reading letters is to think about the question using business ethics.
-First, I formalize the proble.
-Suppose the USPS were a private company that performs a service $S$.
+Suppose that the USPS is an organization  that performs a service $S$.
 Service $S$ takes as input $x$, outputs $S(x)$.

### 2016-05-10 encryption/paper.tex
adsf

@@
 In the process of performing $S$, the USPS does not need to know anything about $x$.
-In fact, I put $x$ into an envelope or letter, call this $l(x)$.
-I actually give the USPS $l(x)$ and they return $S(l(x))$.
-The question then is if the USPS does not need to open $l(x)$ (i.e., reveal $x$) in order to perform $S$, then do they have any right to do so?
+In fact, I put $x$ into an envelope or letter, call this $e(x)$.
+I actually give the USPS $e(x)$ and they return $S(e(x))$.
+The question then is if the USPS does not need to open $e(x)$ (i.e., reveal $x$) in order to perform $S$, then do they have any right to do so?
 
 In a general business setting, I expect that a business will perform what I ask of them with minimal intrusion into inputs.
-I am paying them to perform the service, and not to investigate me.
+I am paying them to perform the service, not to investigate me.
 Perhaps it is reasonable to say that the business can learn some information about $x$ during processing the service, but the amount of that they learn about $x$ should be upper bounded by some value.
@@
 The aim of the government is to aid the people, and this specific case, their foremost goal is deliver my letter or internet request.
-In this light, it seems unreasonable for the USPS or internet provider to open my envelope to read its contents, unless there is some other priority such as national security, which becomes a messier issue.
+In this light, it seems unreasonable for the USPS or internet provider to open my envelope to read its contents, unless there is some other priority such as national security, which makes a messier issue.
 
@@
 This argument is difficult to address for various reasons.
-However, I recall hearing that Snowden revealed that little to none of the NSA's privacy-invading efforts had contributed to national security.
-And that many of the privacy breaches were justified under the guise of national security, but in fact had other uses and purposes.
-To me, this debate in part boils down the efficacy.
+However, I recall hearing that Snowden revealed that little to none of the NSA's privacy-invading efforts had contributed to preventing an attack.
+Snowden also revealed that many of the privacy breaches were justified under the guise of national security, but in fact had other uses and purposes.
+To me, this debate in part boils down to the efficacy of invading privacy towards improving national security.
 There is some sweet spot where privacy and national security are optimized, but the public does not have adequate information to truly assess this problem, as we do not details about national security efforts or privacy invasion.
@@
 
-The first point is that sending messages over the internet is different from talking.
-When people communicate via the internet, the messages are publicly accessible (to some extent), since they bounce from server to server on their way to their destination.
-Talking on the internet is fundamentally different from two parties talking in a private room; rather, they are talking in a crowded room.
-Then, the only possible method by which the parties can achieve privacy is by using public-key encryption, but we must first ask the question: do people have a right to a private conversation in a crowded room?
-In a real world, non-internet setting, I'm inclined to say no. 
-By trying to have a conversation in a crowded room, the parties would inconvenience others, for example by requiring that others steer clear of the section of the room in which the parties are conversing.
-But what if the parties do not inconvenience anyone when having their conversation?
-Encryption on the internet does not inconvenience those with whom the parties am not communicating.
-My conclusion is that there is no easy way to compare encryption to talking.
-At any point, there are differences such that we, as philosophers, lose the ethical importance of the matter when we try to draw parallels.
+In the crowded room hypothetical situation, we concluded that is was unclear, or situational, if we had a right to a private conversation, and our argument was that in order to have a private conversation, we would have to inconvenience others.
+Unfortunately, this hypothetical situation lacks parallelism to using encryption because using encryption does not inconveniene anyone. 
+That is, if I use encryption on the internet, then it has no effect on your internet experience.
+Hence, we must ask the question, if in the hypothetical crowded we hold a private conversation without inconveniencing others, can we?
+One argument arguing in the negation of the question is that it would be rude to leave others out - the others are in the room, and they can listen to our conversation if they want to.
+This argument appeals to the slogan, ``you have nothing to worry about if you have nothing to hide'', where just because I have no reason to have a private conversation, I should not be holding one.
+I am not persuaded by this argument because sometimes I talk and I just don't want a certain group of people to be privy to my convesation.
+If I were not able to prevent a group of people from listening to me, it would restrict what I would say.
+This line of thinking opens a number of questions, such as: by refusing to not eavesdrop, is that group really restricting my speech? Are they restricting my access to speech? 
+Encryption would solve the problem because they could not listen to me and I can say what I want, so do I have a right to encryption if it increases my right or acccess to speech?
+Unfortunately, I lack the time and space to delve into these problems, but they are a sample of the problems that fall out of digging to the crowded room hypothetical.
+Suffice it to say that the crowded room hypothetical is a useful method for approaching the question of encryption.
 
@@
 In section 3.0.3 I introduced formal notation for what it means to send a message $x$ over the internet.
-When a message is sent over the internet, we put the internet into an envelope, creating $l(x)$, such that for the handlers of the internet to read the message they need to open the envelope.
+When a message is sent over the internet, we put the internet into an envelope, creating $e(x)$, such that for the handlers of the internet to read the message they need to open the envelope.
 In the real world, opening the envelope could take many forms; for example, the handlers of the internet could simply save the message after they process it; such an action is above and beyond the duty of the runners of the internet - they do not need to save the message to perform their job, and it doesn't even help them perform their job better - so we should consider such an action as not required.
-This sub-problem is can likely be addressed by appealing to business ethics: to what extent can a business investigate the input to a request from a client without violating the client's privacy?
-
-The third point is that national security is an important consideration.
-Undoubtedly, the internet and encryption could be used to organize events that we have a moral responsibility to prevent, if it is within our power.
-This question ultimatley asks how do we balance the trade-off between national security and privacy.
-Many parties from many perspectives have different beliefs on this question, and I imagine that the problem will continue to be contentious for years to come.
-
-%
-%- Sending messages over the internet is different from talking.
-%    - Same room private conversation
-%    - Same public conversation
-%- Does a business or government have the right to open an envelope?
-%    - Goes back to business ethics and what is infrastructure
-%- National security
-%    - At what point do we have unequivocal right to privacy that trumps any national security argument?
+However, we should not hold internet providers to unreasonable standards.
+For example, it may be useful for the internet provider to save some data about the messages it processes so that it can improve its operations.
+This sub-problem can likely be addressed by appealing to business ethics: to what extent can a business investigate the input to a request from a client without violating the client's privacy?
 
 \section{Conclusion}
-We need to address many other problems before we can come to a good understanding and conclusion to whether we have a right to use encryption over the internet.
-The aim of this paper was to start a formal process for thinking through the question.
+We need to address many problems before we can come to a good understanding and conclusion to whether we have a right to use encryption over the internet.
+The aim of this paper was to start the process for thinking through the question.
 Another easy step forward is see how the arguments for and against encryption fall into the tropes of new and emerging science technology (NEST) ethics.
-We refer the reader to \cite{nest}, a good overview of NEST ethics and common responses.
 

### 2016-05-11 encryption/paper.tex
finished

@@
 
-\title{Creative Destruction in the Philosophy of Technology}
+\title{Do we have a right to encryption?}
 \author{Alex Ledger}
@@
 \section{Introduction}
-Over the last few years, namely since the Snowden revelations in 2013, issues concerning privacy, anonymity and surveillence on the internet have come to the forefront of our cultural discussions.
+Over the last few years, namely since the Snowden revelations in 2013, issues concerning privacy, anonymity and surveillance on the internet have come to the forefront of our cultural discussions.
 Snowden surprised many people when he provided evidence that the NSA has access to our internet activity and specifically that the NSA may read our email, a mode of communication that we commonly considered to be private.
-Due to this new information, many persons seeking privacy from the government resorted to using \textit{encrytion} to protect their privacy.
+Due to this new information, many persons seeking privacy from the government resorted to using \textit{encryption} to protect their privacy.
 Encryption is means of obfuscating a message - if two people use encryption, they can talk to each other without worrying that an eavesdropper might be reading their messages.
@@
 Law-enforcement argues in favor of restricting the power of encryption, and in particular, requiring that all encryption used within the United States have some kind of master-key.
-The master-key, which the company providing the encrpytion would hold (e.g., Apple or Google), would allow law-enforcement agencies to decrypt encrypted messages.
+The master-key, which the company providing the encryption would hold (e.g., Apple or Google), would allow law-enforcement agencies to decrypt encrypted messages.
 
-The goal of this paper is to take a step back from the politicized arguments surrounding encryption and anonymity and ask a basic question: do we have a right to encryption?
+The goal of this paper is to take a step back from the politicized arguments surrounding encryption and ask a basic question: do we have a right to encryption?
 This question is difficult to answer or even approach, and as such, this paper does not answer the question, but it introduces sub-problems that need to be addressed first.
-This paper is a good starting point for thinking about encryption, and is useful for future, rigorous work.
+This paper is a good starting point for thinking about encryption and is useful for future, rigorous work.
 
@@
 Encryption has been around for centuries; we have evidence from centuries ago that various armies used some form of encryption, and more recently and famously, Hitler used the engima machine in World War II to obfuscate messages between his troops.
-It is only recently that society questions unrestricted encryption; my suspicion is that the main reason for this that we all know have access to encryption, as opposed to only states having access, and so encryption needs to be restricted, perhaps to support a state that uses surveillence.
+It is only recently that society questions unrestricted encryption; my suspicion is that the main reason for this is that the public now has access to encryption, as opposed to only states having access, and so encryption needs to be restricted, perhaps to support a state that uses surveillance.
 
@@
 If Apple does not use an encryption scheme with a master-key, a regulatory body could fine Apple for not abiding by the encryption regulations.
-If encryption does become regulated, I predict that some interesting black-market app will appear that performs the same essential functionality as Whatsapp.
+If encryption does become regulated, I predict that some interesting black-market app will appear that performs the same essential functionality as WhatsApp.
 
@@
 For example, it is hard to imagine that the government could successfully prevent any person from using encryption schemes with certain properties, like me using an encryption scheme that I implement myself in Python and use to communicate with my friend.
-The difference between this situation and Apple in the previous paragraph is that I am not selling encrpytion.
-I would imagine that reguations on indivudal encryption would be disallowed by freedom of speech - the freedom to write a program - but I have been surprised by laws and court decisions before.
+The difference between this situation and Apple is that I am not selling encryption.
+I would imagine that regulations on individual encryption would be disallowed by freedom of speech - the freedom to write a program - but I have been surprised by laws and court decisions before.
 
-By requiring encryption schemes that use a master-key, the governemnt would greatly weaken the cyber-security infrastructure.
+By requiring encryption schemes to have a master-key, the government would greatly weaken the cyber-security infrastructure.
 As we have seen, it is not too difficult for hackers, either private or state-sponsored, to break into databases, and in theory, steal the master-key, giving them access to all \textit{private} messages encrypted using that master-key.
@@
 
-\subsubsection{Private Room, Private Converstation}
+\subsubsection{Private Room, Private Conversation}
 If we are alone in a private room with another party, do we have the right to communicate privately - that is, do we have a right to \textit{not} be eavesdropped on?
-To avoid annoying criticisms, let us further assume that we are in a private residence, talking in a soundproof room, and the conversors have received no indication that someone might be listening to our conversation.
+To avoid annoying criticisms, let us further assume that we are in a private residence, talking in a soundproof room, and we have received no indication that someone might be listening to our conversation.
 In this case, it seems reasonable to expect a private conversation.
-However, the internet is not a private room with only two parties; rather, it may be considered a crowded place, so this hypothetical situation lacks a strong parellel to actual usage of encryption.
+However, the internet is not a private room with only two parties; rather, it may be considered a crowded place, so this hypothetical situation lacks a strong parallel to actual usage of encryption.
 
@@
 For instance, it seems weird that we expect to have a private conversation in such a situation: why would we not move to a different room to talk privately?
-On the other hand, if we assume that room is public and we don't have access to a private room, then we need to section of a portion of the room for our private use.
-This would inconvience others in the room, only for the sake of our private conversation.
-In some situations, if our private conversation is critical for the people in the room, then it is justified for us to inconvenience the others, but in general, it does not seem justified.
+On the other hand, if we assume that room is public and we don't have access to a private room, then we need to section off a portion of the room for our private use.
+This would inconvenience others in the room, only for the sake of our private conversation.
+In some situations, if our private conversation is critical for the safety of the people in the room, then it is justified for us to inconvenience the others, but in general, it does not seem justified.
 It does not seem that we necessarily have a right to a private conversation; the right to the private conversation is situational.
@@
 The matter is complicated by the fact that we don't \textit{own} the internet; the internet is run by private firms and the government, and they let us use it (for a price or taxes). 
-This makes communicating over the internet similar to communicating via the United States Post Service USPS.
+This makes communicating over the internet similar to communicating via the United States Post Service (USPS).
 I give my letter to the USPS and tell them a desired destination, the USPS does internal work to get the letter to the destination, and you eventually receive the letter.
@@
 Does the postal service have the right to open up my letter and read it?
-I believe - but may be wrong - that most people feel that the USPS should not be able to open my letter and read it. 
-My letter is private, and I am paying them for their communication services, so they should communicate my letter without meddling.
+I believe - but may be wrong - that most people feel that the USPS should not open my letter and read its contents. 
+My letter is private, and I am paying them for their communication services, so they should service my letter without meddling.
 
@@
 In the process of performing $S$, the USPS does not need to know anything about $x$.
-In fact, I put $x$ into an envelope or letter, call this $e(x)$.
+I could put $x$ into an envelope or letter, call this $e(x)$.
 I actually give the USPS $e(x)$ and they return $S(e(x))$.
@@
 
-In a general business setting, I expect that a business will perform what I ask of them with minimal intrusion into inputs.
-I am paying them to perform the service, not to investigate me.
-Perhaps it is reasonable to say that the business can learn some information about $x$ during processing the service, but the amount of that they learn about $x$ should be upper bounded by some value.
-That is, they can learn some things, because it's unreasonable to hold them an absurdly high standard of respecting my privacy, but they shouldn't go out of their way to learn about my input.
+In a general business setting, I expect that a business will perform what I ask of them with minimal intrusion into the input, $x$: I am paying them to perform the service, not to investigate me.
+Perhaps it is reasonable to say that the business can learn some information about $x$ during processing the service, but the amount that they learn about $x$ should be upper bounded by some value.
+That is, they can learn some things, because it is unreasonable to hold them an absurdly high standard of respecting my privacy, but they should not go out of their way to learn about my input.
 
@@
 To me, this debate in part boils down to the efficacy of invading privacy towards improving national security.
-There is some sweet spot where privacy and national security are optimized, but the public does not have adequate information to truly assess this problem, as we do not details about national security efforts or privacy invasion.
+There is some sweet spot where the trade-off between privacy and national security is optimized, but the public does not have adequate information to truly assess this problem, as we do not details about national security efforts or privacy invasion.
 
@@
 In the crowded room hypothetical situation, we concluded that is was unclear, or situational, if we had a right to a private conversation, and our argument was that in order to have a private conversation, we would have to inconvenience others.
-Unfortunately, this hypothetical situation lacks parallelism to using encryption because using encryption does not inconveniene anyone. 
+Unfortunately, this hypothetical situation lacks parallelism to using encryption because using encryption does not inconvenience anyone. 
 That is, if I use encryption on the internet, then it has no effect on your internet experience.
-Hence, we must ask the question, if in the hypothetical crowded we hold a private conversation without inconveniencing others, can we?
-One argument arguing in the negation of the question is that it would be rude to leave others out - the others are in the room, and they can listen to our conversation if they want to.
+Hence, we must ask the question, if we can hold a private conversation in the crowded room without inconveniencing others, should we?
+One argument in the negation of the question is that it would be rude to leave others out - the others are in the room, and they can listen to our conversation if they want to.
 This argument appeals to the slogan, ``you have nothing to worry about if you have nothing to hide'', where just because I have no reason to have a private conversation, I should not be holding one.
-I am not persuaded by this argument because sometimes I talk and I just don't want a certain group of people to be privy to my convesation.
+I am not persuaded by this argument because sometimes I talk and I just don't want a certain group of people to be privy to my conversation.
 If I were not able to prevent a group of people from listening to me, it would restrict what I would say.
 This line of thinking opens a number of questions, such as: by refusing to not eavesdrop, is that group really restricting my speech? Are they restricting my access to speech? 
-Encryption would solve the problem because they could not listen to me and I can say what I want, so do I have a right to encryption if it increases my right or acccess to speech?
+Encryption would solve the problem because they could not listen to me and I can say what I want, so do I have a right to encryption if it increases my right or access to speech?
 Unfortunately, I lack the time and space to delve into these problems, but they are a sample of the problems that fall out of digging to the crowded room hypothetical.
@@
 When a message is sent over the internet, we put the internet into an envelope, creating $e(x)$, such that for the handlers of the internet to read the message they need to open the envelope.
-In the real world, opening the envelope could take many forms; for example, the handlers of the internet could simply save the message after they process it; such an action is above and beyond the duty of the runners of the internet - they do not need to save the message to perform their job, and it doesn't even help them perform their job better - so we should consider such an action as not required.
-However, we should not hold internet providers to unreasonable standards.
-For example, it may be useful for the internet provider to save some data about the messages it processes so that it can improve its operations.
+In the real world, opening the envelope could take many forms; for example, the handlers of the internet could simply save the message after they process it; such an action is above and beyond the duty of the runners of the internet - they do not need to save the message to perform their job, but it may be useful for the internet provider to save some data about the messages it processes so that it can improve its operations.
 This sub-problem can likely be addressed by appealing to business ethics: to what extent can a business investigate the input to a request from a client without violating the client's privacy?
@@
 The aim of this paper was to start the process for thinking through the question.
-Another easy step forward is see how the arguments for and against encryption fall into the tropes of new and emerging science technology (NEST) ethics.
+Another easy step forward is see how the arguments for and against encryption fall into the tropes of new and emerging science and technology (NEST) ethics.
 
